### 2021-02-17 outputs/Paper.Rmd
main structure

---
title: "TITLE"
author: "Adrian Wong, Yingying Zhou, Xinyi Xu, Yang Wu "
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 bookdown::pdf_document2:
 toc: no
subtitle: "SUBTITLE"
abstract: "ABSTRACT"
thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# Introduction
```{r}

```

# Data

## Intervention

## Data Gathering Method

## Descriptive Analysis

```{r}

```

# Discussion

## Overview

## Findings

### Finding ONE

### Finding TWO

### Finding THREE

## Limitation

## Future Directions

```{r}

```

\newpage

# References

### 2021-02-18 scripts/survey_response_simulation.R
Added correlation matrix for columns 6, 10, and 14 (will add more once data is cleaned)

@@ -10,6 +10,8 @@
 
 #### Workspace setup ####
 library(tidyverse)
+#install.packages("PerformanceAnalytics")
+library("PerformanceAnalytics")
 
 
 # Function that takes a region and generates a random FSA code within that region
@@ -280,8 +282,7 @@ simulated_dataset_control<- rbind(small_restaurant_c,big_restaurant_c)
 simulated_dataset <-
   rbind(simulated_dataset_control, simulated_dataset_treated)
 
-# Is there a more efficient way to do this?
-# I essentially loop through all of the rows and generate an FSA code based on the row's region
+# Loop through all of the rows and generate an FSA code based on the row's region
 for (i in 1:nrow(simulated_dataset)){
   simulated_dataset$Q1[i] = fsa_generate(simulated_dataset$Q2[i])
 }
@@ -301,6 +302,8 @@ revenue_c <- simulated_dataset_control$Q13
 revenue_t <- simulated_dataset_treated$Q13
 t.test(revenue_c, revenue_t)
 
+#### Correlation Matrix ####
+chart.Correlation(simulated_dataset[c(6, 10, 14)], histogram=TRUE)
 
 #### Make some graphs very quickly
 
@@ -312,8 +315,6 @@ simulated_dataset %>%
   theme_minimal() +
   facet_wrap(vars(type))
 
-
-
 simulated_dataset %>% 
   ggplot(aes(x = Q3)) +
   geom_bar(stat="count") +
@@ -321,7 +322,6 @@ simulated_dataset %>%
   labs(x = "Restaurant type",
        y = "Number of restaurants") +
   scale_fill_brewer(palette = "Set1")
-
 
 simulated_dataset %>% 
   ggplot(aes(x = Q5)) +
@@ -332,7 +332,7 @@ simulated_dataset %>%
   scale_color_brewer(palette = "Set1")
 
 simulated_dataset %>% 
-  ggplot(aes(x = Q1, y = type, color=Q1)) +
+  ggplot(aes(x = Q2, y = type, color=Q2)) +
   geom_jitter(show.legend = FALSE) +
   labs(title = "Experimental Conditions across Regions", x = "Region", y = "Experimental Condition") +
   theme_minimal()

### 2021-02-18 scripts/survey_response_simulation.R
Control group no longer has rows with no delivery and no takeout

@@ -284,7 +284,18 @@ simulated_dataset <-
 
 # Loop through all of the rows and generate an FSA code based on the row's region
 for (i in 1:nrow(simulated_dataset)){
+  rand = sample(x=c(1,2,3), prob=c(0.33, 0.33, 0.33))
   simulated_dataset$Q1[i] = fsa_generate(simulated_dataset$Q2[i])
+  if (simulated_dataset$Q6[i] == "No" && simulated_dataset$Q7[i] == "No") {
+    if (rand == 1) {
+      simulated_dataset$Q6[i] = "Yes"
+    } else if (rand == 2){
+      simulated_dataset$Q7[i] = "Yes"
+    } else {
+      simulated_dataset$Q6[i] = "Yes"
+      simulated_dataset$Q7[i] = "Yes"
+    }
+  }
 }
 
 # Order Q1 before Q2 (not actually necessary)

### 2021-02-18 scripts/survey_response_simulation.R
Control group no longer has rows with no delivery and no takeout

@@ -283,10 +283,15 @@ simulated_dataset <-
   rbind(simulated_dataset_control, simulated_dataset_treated)
 
 # Loop through all of the rows and generate an FSA code based on the row's region
+# Also fix simulated data fro Q6 and Q7 - control group must have either takeout or delivery
+# or else they would be closed and not be a part of this survey
 for (i in 1:nrow(simulated_dataset)){
-  rand = sample(x=c(1,2,3), prob=c(0.33, 0.33, 0.33))
   simulated_dataset$Q1[i] = fsa_generate(simulated_dataset$Q2[i])
-  if (simulated_dataset$Q6[i] == "No" && simulated_dataset$Q7[i] == "No") {
+  
+  # Pick a random number between 1 and 3 inclusive
+  # Assigns Q6, Q7, or both as "Yes" depending on the rand number
+  rand = sample(x=c(1,2,3), prob=c(0.33, 0.33, 0.33))
+  if (simulated_dataset$Q6[i] == "No" && simulated_dataset$Q7[i] == "No" && simulated_dataset$type[i] == "Control") {
     if (rand == 1) {
       simulated_dataset$Q6[i] = "Yes"
     } else if (rand == 2){

### 2021-02-22 outputs/Paper.Rmd
update

@@
 thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
+bibliography: references.bib
 ---
@@
 library(tidyverse)
+#install.packages("PerformanceAnalytics")
+library("PerformanceAnalytics")
+
 ```

### 2021-02-22 scripts/survey_response_simulation.R
update

@@ -313,6 +313,10 @@ write_csv(simulated_dataset, 'inputs/simulated_data.csv')
 
 
 #### Exploratory Data Analysis ####
+
+
+
+
 #### Statistical Inference ####
 revenue_c <- simulated_dataset_control$Q13
 revenue_t <- simulated_dataset_treated$Q13

### 2021-02-22 outputs/Paper.Rmd
update

@@
 
-```{r}
+```{r read_data, include=FALSE}
+
+setwd("~/Downloads/Git/groupproject-")
+
+# read raw dataset from scripts, need to run survey_response _simulation first.
+simulated_data<- read_csv("inputs/simulated_data.csv")
+
+# We add a new column To distinguish the restaurant size by employees number. 
+# if employees number >20 then we define it is big, otherwise it is small.
+for (i in 1:nrow(simulated_data)){
+  if ((simulated_data$Q8[i] == ">30") || (simulated_data$Q8[i] == "20-30")){
+  simulated_data$size[i] = "Big"  
+  }else {
+    simulated_data$size[i] = "Small"
+  }
+}
+
+treated_data<-
+  filter(simulated_data, simulated_data$type == "Treated" ) # load treated data
+
+control_data<-
+  filter(simulated_data, simulated_data$type == "Control" ) # load control data
+```
+
+### Revenue distributions group by restaurant size
+```{r revenue_distribution, echo=FALSE}
+
+library(ggplot2)
+# Treated group
+rd1<-
+  ggplot(treated_data, aes(x = treated_data$Q13)) +
+  geom_histogram(aes(color = size, fill= size),
+                position = "identity", bins = 40, alpha=0.5) +
+  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
+  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
+  labs(title="Revenue Distributions in Treated Group", x="Renvenue", y="Count")+
+  geom_density(alpha=.2, fill="#FF6666")+
+  theme_linedraw()
+# Control group
+rd2<-
+  ggplot(control_data, aes(x = control_data$Q13)) +
+  geom_histogram(aes(color = size, fill= size),
+                position = "identity", bins = 40, alpha=0.5) +
+  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
+  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
+  labs(title="Revenue Distributions in Control Group", x="Renvenue", y="Count")+
+  geom_density(alpha=.2, fill="#FF6666")+
+  theme_linedraw()
+# combine two diagram in one graph
+#install.packages("ggpubr")
+library(ggpubr)
+ggarrange(
+  rd1, rd2, 
+  ncol = 1, nrow = 2,
+  heights = c(1, 1),
+  align = "hv",
+  common.legend = TRUE, legend = "bottom"
+  )
 
 ```
-
 # Discussion

### 2021-02-22 scripts/survey_response_simulation.R

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: This script simulates the responses to a survey about restaurants in Toronto.
-# Author: Yingying Zhou, Xinyi Xu
+# Author: Yingying Zhou, Xinyi Xu, Yang Wu 
 # Data: 14 February 2021
-# Contact: yingying.zhou@utoronto.ca; xiny.xu@mail.utoronto.ca; 
+# Contact: yingying.zhou@utoronto.ca; xiny.xu@mail.utoronto.ca; yangg.wu@mail.urotonto.ca
 # License: MIT
 # Pre-requisites: 
 # - None
@@ -103,6 +103,7 @@ fsa_generate <- function(region) {
 # Q11: How has your FIXED costs to run the restaurant changed within this month?
 # Q12: How has your FLEX/VARIABLE costs to run the restaurant changed within this month?
 # Q13: How much revenue did your restaurant make in the past month? ($CAD)
+
 
 # Do this one for treated and once for control and then bring them together
 

### 2021-02-23 outputs/Paper.Rmd
update

@@
 ```
+
+### restaurant type by regions
+
+```{r restaurant_type, echo=FALSE}
+
+library(viridis)
+
+# Treated group
+rt1<-
+  ggplot(treated_data, aes(fill= Q3, x= Q2)) +
+  geom_bar(position="stack", stat="count")+
+    ggtitle("Treated Group: Restaurant Types in different regions") +
+    xlab("Regions")+
+    ylab("Count of Numbers")+
+    theme_grey()
+
+rt1<- rt1 + guides(fill=guide_legend(title="Types")) # change the Legend title
+
+# Control group
+rt2<-
+  ggplot(control_data, aes(fill= Q3, x= Q2)) +
+  geom_bar(position="stack", stat="count")+
+    ggtitle("Control Group: Restaurant Types in different regions") +
+    xlab("Regions")+
+    ylab("Count of Numbers")+
+    theme_grey()
+
+rt2<- rt2 + guides(fill=guide_legend(title="Types")) # change the Legend title 
+# combine two diagram in one graph
+ggarrange(
+  rt1, rt2, 
+  ncol = 2, nrow = 1,
+  vjust = 1,
+  widths = c(2, 2),
+  align = "hv",
+  common.legend = TRUE, legend = "bottom"
+  )
+
+```
+
+### Flex and fiexed cost changes
+
+```{r felx_fix, echo=FALSE, fig.width=10, fig.height=4}
+
+# Treated group
+
+# Fixed costs 
+fixc1<-
+  ggplot(treated_data, aes(fill= Q11, x=Q11)) +
+  geom_bar(stat="count", width = 0.5)+
+    ggtitle("Fixed costs changes") +
+    coord_flip()+
+    xlab("Changes")+
+    ylab("Number of restaurants")+
+    theme_minimal()
+
+fixc1<- fixc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title
+
+# flex cost
+flexc1<-
+    ggplot(treated_data, aes(fill= Q12, x=Q12)) +
+    geom_bar(stat="count", width = 0.5)+
+    ggtitle("Treated Group: Flexible costs changes") +
+    coord_flip()+
+    xlab("Changes")+
+    ylab("Number of restaurants")+
+    theme_minimal()
+
+flexc1<- flexc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title
+
+# Control group
+fixc2<-
+  ggplot(control_data, aes(fill= Q11, x=Q11)) +
+  geom_bar(stat="count", width = 0.5)+
+    ggtitle("Fixed costs changes") +
+    coord_flip()+
+    xlab("Changes")+
+    ylab("Number of restaurants")+
+    theme_minimal()
+
+fixc2<- fixc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title
+
+# flex cost
+flexc2<-
+    ggplot(control_data, aes(fill= Q12, x=Q12)) +
+    geom_bar(stat="count", width = 0.5)+
+    ggtitle("Control Group: Flexible costs changes") +
+    coord_flip()+
+    xlab("Changes")+
+    ylab("Number of restaurants")+
+    theme_minimal()
+
+flexc2<- flexc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title
+
+# combine two diagram in one graph
+ggarrange(
+  flexc1,fixc1,flexc2, fixc2,
+  ncol = 2, nrow = 2,
+  vjust = 1,
+  widths = c(2, 2),
+  align = "hv",
+  common.legend = TRUE, legend = "bottom"
+  )
+
+```
+
+### Distribution average employee salary
+```{r salary_distribution, echo=FALSE, fig.width=10, fig.height=4}
+library(ggthemes)
+# Treated group
+s1<-
+  ggplot(treated_data, aes(x = Q2, y= Q9)) +
+  geom_boxplot(outlier.colour="red", 
+               outlier.shape=5,
+               outlier.size=4) +
+  labs(title="Salary Distributions in Treated Group", x="Regions", y="Hourly rate")+
+  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ # add dots
+  theme_economist()
+
+# Control group
+s2<-
+  ggplot(control_data, aes(x = Q2, y= Q9)) +
+  geom_boxplot(outlier.colour="red", 
+               outlier.shape=5,
+               outlier.size=4) +
+  labs(title="Salary Distributions in Control Group", x="Regions", y="Hourly rate")+
+  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ #add dots
+  theme_economist()
+
+# combine two diagram in one graph
+
+library(ggpubr)
+ggarrange(
+  s1, s2, 
+  ncol = 2, nrow = 1,
+  hjust = -0.5,
+  align = "hv"
+  )
+
+```
+
+### correlation matrix
+```{r correlation, echo=FALSE, fig.width=10, fig.height=4}
+
+```
+
 # Discussion

### 2021-02-23 outputs/Paper.Rmd
Appendix Update

--- 2021-02-22 outputs/Paper.Rmd
@@
 thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
-bibliography: references.bib
 ---
@@
 library(tidyverse)
-#install.packages("PerformanceAnalytics")
-library("PerformanceAnalytics")
-
 ```
@@
 \newpage
+# Appendix
+
+## Appendix A
+```{r AppendixA, message=FALSE, echo = FALSE}
+### Number in GTA ### 
+number_of_Toronto = 7500
+number_of_Durham = 3260
+number_of_York = 5553
+number_of_Peel = 6235
+number_of_Halton = 2803
+number_of_GTA = sum(number_of_Toronto,number_of_Durham,number_of_York,number_of_Peel,number_of_Halton)
+
+### Proportion ###
+proportion_Toronto = (number_of_Toronto/number_of_GTA*100) 
+proportion_Durham = (number_of_Durham/number_of_GTA*100)
+proportion_York = (number_of_York/number_of_GTA*100)
+proportion_Peel = (number_of_Peel/number_of_GTA*100)
+proportion_Halton = (number_of_Halton/number_of_GTA*100)
+Proportion_GTA = (number_of_GTA /number_of_GTA*100)
+
+### Number of Sample ###
+number_of_sample = 1637
+
+sample_Toronto =proportion_Toronto*number_of_sample
+sample_Durham =proportion_Durham *number_of_sample
+sample_York =proportion_York*number_of_sample
+sample_Peel =proportion_Peel*number_of_sample
+sample_Halton =proportion_Halton *number_of_sample
+
+### Dataframe ###
+sample_size <- data.frame(
+  Region = c ("Toronto", "Durham" , "York" , "Peel" , "Halton","Total"),
+  Number_of_Region = c (number_of_Toronto,number_of_Durham,number_of_York,number_of_Peel,number_of_Halton,number_of_GTA),
+  Proportion_of_Region= c (proportion_Toronto,proportion_Durham,proportion_York,proportion_Peel,proportion_Halton,Proportion_GTA)%>% round(digits = 2),
+  Sample_of_Region = c (sample_Toronto,sample_Durham,sample_York ,sample_Peel,sample_Halton,number_of_sample) %>% round(digits = 0)
+  )
+
+### Table ###
+library(kableExtra)
+sample_size %>% 
+  knitr::kable(caption = "Detailed information for stratification",
+               col.names = c("Region", "Number of Restuarants", "Proportion(%)", "Sample Selected"))%>%
+  kable_styling()
+```
+
+## Appendix B
+```{r AppendixB, message=FALSE, echo = FALSE}
+### basic information ###
+number_of_survey = 3454
+number_of_consent = 11325
+
+print_cost_per_page = 0.05 
+envelope_cost = 0.15
+one_way_stamp = 0.55
+
+### Calculation ###
+
+total_print_cost = print_cost_per_page* (number_of_consent+number_of_survey)
+total_envelope_cost = (number_of_consent+number_of_survey)*envelope_cost*2
+total_stamp_cost =(number_of_consent+number_of_survey)*one_way_stamp*2
+
+total_cost = total_print_cost+total_envelope_cost+total_stamp_cost
+
+### dataframe ###
+estimated_cost <- data.frame(
+  Components = c ("Printing Cost", "Envelope Cost", "Stamp Cost"),
+  Cost_per_unit= c (print_cost_per_page,envelope_cost,one_way_stamp),
+  Total_cost_of_each_component  = c (total_print_cost, total_envelope_cost, total_stamp_cost)
+)
+
+### Table  ###
+library(kableExtra)
+estimated_cost %>% 
+  knitr::kable(caption = "Estimated Cost",
+               col.names = c("Components", "Cost per unit", "Total cost for each component"))%>%
+  kable_styling()
+
+```
+
+\newpage
 

### 2021-02-25 outputs/Paper.Rmd
update

--- 2021-02-23 outputs/Paper.Rmd
@@
 library(ggplot2)
+library(ggthemes)
 # Treated group
@@
   geom_histogram(aes(color = size, fill= size),
-                position = "identity", bins = 40, alpha=0.5) +
+                position = "identity", bins = 30, alpha=0.5) +
   scale_color_manual(values = c("#00AFBB", "#E7B800")) +
@@
   geom_density(alpha=.2, fill="#FF6666")+
-  theme_linedraw()
+  theme_calc()
 # Control group
@@
   geom_density(alpha=.2, fill="#FF6666")+
-  theme_linedraw()
+  theme_calc()
 # combine two diagram in one graph
@@
 
-```{r restaurant_type, echo=FALSE}
+```{r restaurant_type, echo=FALSE,fig.width=12, fig.height=4}
 
@@
   geom_bar(position="stack", stat="count")+
-    ggtitle("Treated Group: Restaurant Types in different regions") +
+    ggtitle("Treated Group: Restaurant Types") +
     xlab("Regions")+
@@
   geom_bar(position="stack", stat="count")+
-    ggtitle("Control Group: Restaurant Types in different regions") +
+    ggtitle("Control Group: Restaurant Types") +
     xlab("Regions")+
@@
 ### correlation matrix
-```{r correlation, echo=FALSE, fig.width=10, fig.height=4}
+```{r correlation, echo=FALSE, fig.width=20, fig.height=20}
+#install.packages("fastDummies")
+library(fastDummies)
+Dummy_data<-simulated_data[-c(1,2,10)]
+
+Dummy_data<- fastDummies::dummy_cols(Dummy_data)
+
+# correlation matrix for Big restaurants
+Dummy_data<-Dummy_data[-c(1:3,5:10,12,43)]
+
+# Compute a correlation matrix
+corr <- round(cor(Dummy_data), 1)
+
+# Compute a matrix of correlation p-values
+#install.packages("ggcorrplot")
+library(ggcorrplot)
+p.mat <- cor_pmat(Dummy_data)
+
+# Visualize the lower triangle of the correlation matrix
+# Barring the no significant coefficient
+corr.plot1 <- ggcorrplot(
+  corr, hc.order = TRUE, type = "lower",
+  p.mat=p.mat
+  )
+corr.plot1
+
+# correlation matrix for Small restaurants
+Dummy_data<-simulated_data[-c(1,2,10)]
+Dummy_data<- fastDummies::dummy_cols(Dummy_data)
+Dummy_data<-Dummy_data[-c(1:3,5:10,12,42)]
+
+# Compute a correlation matrix
+corr <- round(cor(Dummy_data), 1)
+
+# Compute a matrix of correlation p-values
+library(ggcorrplot)
+p.mat <- cor_pmat(Dummy_data)
+
+# Visualize the lower triangle of the correlation matrix
+# Barring the no significant coefficient
+corr.plot2 <- ggcorrplot(
+  corr, hc.order = TRUE, type = "lower",
+  p.mat=p.mat
+  )
+corr.plot2
+
+# combine two diagram in one graph
+
+ggarrange(
+  corr.plot1, corr.plot2, 
+  labels = c('Big restaurant', 'Small restaurant'),
+  ncol = 2, nrow = 1,
+  align = "hv"
+  )
 

### 2021-02-25 outputs/Paper.Rmd
update

@@
 ## Descriptive Analysis
-
 ```{r read_data, include=FALSE}
@@
 ```
+
+```{r size,echo=FALSE}
+# Get the number of rows
+size<- nrow(simulated_data)
+```
+
+After discussing data gathering method, we sampled data in R. We totally have **`r size`** observations, and 14 of following features according to the questionnaires.
+
+* `type` : Unique row identifier for Open Data database
+* `Q1` : Unique row identifier for Open Data database
+* `Q2` : Unique row identifier for Open Data database
+* `Q3` : Unique row identifier for Open Data database
+* `Q4` : Unique row identifier for Open Data database
+* `Q5` : Unique row identifier for Open Data database
+* `Q6` : Unique row identifier for Open Data database
+* `Q7` : Unique row identifier for Open Data database
+* `Q8` : Unique row identifier for Open Data database
+* `Q9` : Unique row identifier for Open Data database
+* `Q10` : Unique row identifier for Open Data database
+* `Q11` : Unique row identifier for Open Data database
+* `Q12` : Unique row identifier for Open Data database
+* `Q13` : Unique row identifier for Open Data database
+* `Q14` : Unique row identifier for Open Data database
 

### 2021-02-25 outputs/Paper.Rmd

@@
 library("PerformanceAnalytics")
+library(ggplot2)
+library(kableExtra)
 
@@
 
-After discussing data gathering method, we sampled data in R. We totally have **`r size`** observations, and 14 of following features according to the questionnaires.
+After discussing data gathering method, we sampled data in R [@citeR]. We totally have **`r size`** observations, and 14 of following features according to the questionnaires.
 

### 2021-02-25 outputs/Paper.Rmd
update

@@
 
-* `type` : Unique row identifier for Open Data database
-* `Q1` : Unique row identifier for Open Data database
-* `Q2` : Unique row identifier for Open Data database
-* `Q3` : Unique row identifier for Open Data database
-* `Q4` : Unique row identifier for Open Data database
-* `Q5` : Unique row identifier for Open Data database
-* `Q6` : Unique row identifier for Open Data database
-* `Q7` : Unique row identifier for Open Data database
-* `Q8` : Unique row identifier for Open Data database
-* `Q9` : Unique row identifier for Open Data database
-* `Q10` : Unique row identifier for Open Data database
-* `Q11` : Unique row identifier for Open Data database
-* `Q12` : Unique row identifier for Open Data database
-* `Q13` : Unique row identifier for Open Data database
-* `Q14` : Unique row identifier for Open Data database
+* `type` : Categorical identifier [“Treated” or “Control”] for each observation 
+* `Q1` : First three digitals of the postcode 
+* `Q2` : Categorical identifier for distinguishing the type of restaurants 
+* `Q3` : Region name in GTA
+* `Q4` : Describe whether the restaurant is a franchise (“Franchise” or “No”)
+* `Q5` : The length of the operation years for each restaurant 
+* `Q6` : Describe whether the restaurant offer takeout service (“Yes” or “No”)
+* `Q7` : Describe whether the restaurant offer delivery service (“Yes” or “No”)
+* `Q8` : Number of employees in the restaurant (category type)
+* `Q9` : Average employee hourly rate (CAD) 
+* `Q10` : Describe whether the restaurant has been a site of a potential COVID case (“Yes” or “No”)
+* `Q11` : Describe the restaurant’s fixed costs change situation 
+* `Q12` :  Describe the restaurant’s flexible costs change situation 
+* `Q13` : The restaurant’s past month revenue (CAD)
+
+The first six rows of raw data is shown in the table1 below. (Table \@ref(tab:rowdata))
+```{r rowdata, echo=FALSE}
+#plot row data set in table
+  head(simulated_data)%>%
+  select(-size)%>%
+  kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
+  kableExtra::kable_styling(latex_options = "scale_down") # use scale_down option to make the font
+```
 

### 2021-02-25 outputs/Paper.Rmd
update

@@
 #plot row data set in table
-  head(simulated_data)%>%
+  head(simulated_data,10)%>%
   select(-size)%>%
   kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
-  kableExtra::kable_styling(latex_options = "scale_down") # use scale_down option to make the font
+  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
+  kable_styling()
 ```

### 2021-02-25 outputs/Paper.Rmd
update t test

--- 2021-02-25 outputs/Paper.Rmd
@@
 
-The first six rows of raw data is shown in the table1 below. (Table \@ref(tab:rowdata))
+The first six rows of raw data is shown in the Table1. (Table \@ref(tab:rowdata))
 ```{r rowdata, echo=FALSE}
@@
   kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
-  kableExtra::kable_styling(latex_options = "scale_down") # use scale_down option to make the font
+  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
+  kable_styling()
 ```
+### T-Test
+```{r ttest,echo=FALSE}
+#install.packages("broom")
+library(broom)
+revenue_c <- control_data$Q13
+revenue_t <- treated_data$Q13
+t<-t.test(revenue_t, revenue_c)
+m<-tidy(t, digits=1)
+m%>%
+  select(-c(estimate,statistic,parameter))%>%
+  rename(
+    mean_of_Treated=estimate1,
+    mean_of_Control=estimate2
+  )%>%
+  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
+  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
+  kable_styling()
+
+```
+The T Test is used to compare the sample mean of our Treated group and Control group.
+The goal is to determine whether the intervention has an effective effect on the treated group.
+Our hypothesis is the intervention will have positive impact towards the restaurant's revenue.
+[@kim2015t] The T test results is represented in the Table2(Table \@ref(tab:ttest)).
+The package **Broom**[@broom1] is used to clean the t test results and convert it into the dataframe.
+The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant).[@kim2015t] So we can
+interpret hypothesis not rejected which means the intervention has a significant effect on treated group.
 
@@
 ```{r revenue_distribution, echo=FALSE}
-
 library(ggplot2)
@@
   )
-
 ```

### 2021-02-26 outputs/Paper.Rmd
update graphs

@@
 library(kableExtra)
-
+library(ggpubr)
 ```
@@
 ```
-### T-Test
-```{r ttest,echo=FALSE}
-#install.packages("broom")
-library(broom)
-revenue_c <- control_data$Q13
-revenue_t <- treated_data$Q13
-t<-t.test(revenue_t, revenue_c)
-m<-tidy(t, digits=1)
-m%>%
-  select(-c(estimate,statistic,parameter))%>%
-  rename(
-    mean_of_Treated=estimate1,
-    mean_of_Control=estimate2
-  )%>%
-  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
-  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
-  kable_styling()
+### EDA
 
-```
-The T Test is used to compare the sample mean of our Treated group and Control group.
-The goal is to determine whether the intervention has an effective effect on the treated group.
-Our hypothesis is the intervention will have positive impact towards the restaurant's revenue.
-[@kim2015t] The T test results is represented in the Table2(Table \@ref(tab:ttest)).
-The package **Broom**[@broom1] is used to clean the t test results and convert it into the dataframe.
-The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant).[@kim2015t] So we can
-interpret hypothesis not rejected which means the intervention has a significant effect on treated group.
+```{r restaurant_number, echo=FALSE, fig.width=6, fig.height=5}
+R1<-simulated_data%>%
+  ggplot(aes(x = simulated_data$Q2,fill = type)) +
+  geom_bar(stat = "count", position = "dodge") +
+  labs(title = "More restuarants are loacted in City of Toronto and Peel Region",x="Regions") +
+  theme_minimal() +
+  scale_fill_manual(values = c("Red", "Blue"))
 
-### Revenue distributions group by restaurant size
-```{r revenue_distribution, echo=FALSE}
-library(ggplot2)
-library(ggthemes)
-# Treated group
-rd1<-
-  ggplot(treated_data, aes(x = treated_data$Q13)) +
-  geom_histogram(aes(color = size, fill= size),
-                position = "identity", bins = 30, alpha=0.5) +
-  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
-  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
-  labs(title="Revenue Distributions in Treated Group", x="Renvenue", y="Count")+
-  geom_density(alpha=.2, fill="#FF6666")+
-  theme_calc()
-# Control group
-rd2<-
-  ggplot(control_data, aes(x = control_data$Q13)) +
-  geom_histogram(aes(color = size, fill= size),
-                position = "identity", bins = 30, alpha=0.5) +
-  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
-  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
-  labs(title="Revenue Distributions in Control Group", x="Renvenue", y="Count")+
-  geom_density(alpha=.2, fill="#FF6666")+
-  theme_calc()
+R2<-simulated_data%>%
+  ggplot(aes(x = simulated_data$Q3 ,fill = type)) +
+  geom_bar(stat = "count", position = "dodge") +
+  labs(title = "More restuarants in GTA are casual dinning ",x="Regions") +
+  theme_minimal() +
+  scale_fill_manual(values = c("Red", "Blue"))
+
 # combine two diagram in one graph
-#install.packages("ggpubr")
-library(ggpubr)
 ggarrange(
-  rd1, rd2, 
+  R1,R2,
   ncol = 1, nrow = 2,
-  heights = c(1, 1),
+  vjust = 1,
+  widths = c(2, 2),
   align = "hv",
@@
 
-### restaurant type by regions
-
 ```{r restaurant_type, echo=FALSE,fig.width=12, fig.height=4}
 
-library(viridis)
+library(viridisLite)
 
@@
 
-### Flex and fiexed cost changes
-
-```{r felx_fix, echo=FALSE, fig.width=10, fig.height=4}
-
-# Treated group
-
-# Fixed costs 
-fixc1<-
-  ggplot(treated_data, aes(fill= Q11, x=Q11)) +
-  geom_bar(stat="count", width = 0.5)+
-    ggtitle("Fixed costs changes") +
-    coord_flip()+
-    xlab("Changes")+
-    ylab("Number of restaurants")+
-    theme_minimal()
-
-fixc1<- fixc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title
-
-# flex cost
-flexc1<-
-    ggplot(treated_data, aes(fill= Q12, x=Q12)) +
-    geom_bar(stat="count", width = 0.5)+
-    ggtitle("Treated Group: Flexible costs changes") +
-    coord_flip()+
-    xlab("Changes")+
-    ylab("Number of restaurants")+
-    theme_minimal()
-
-flexc1<- flexc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title
-
-# Control group
-fixc2<-
-  ggplot(control_data, aes(fill= Q11, x=Q11)) +
-  geom_bar(stat="count", width = 0.5)+
-    ggtitle("Fixed costs changes") +
-    coord_flip()+
-    xlab("Changes")+
-    ylab("Number of restaurants")+
-    theme_minimal()
-
-fixc2<- fixc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title
-
-# flex cost
-flexc2<-
-    ggplot(control_data, aes(fill= Q12, x=Q12)) +
-    geom_bar(stat="count", width = 0.5)+
-    ggtitle("Control Group: Flexible costs changes") +
-    coord_flip()+
-    xlab("Changes")+
-    ylab("Number of restaurants")+
-    theme_minimal()
-
-flexc2<- flexc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title
-
-# combine two diagram in one graph
-ggarrange(
-  flexc1,fixc1,flexc2, fixc2,
-  ncol = 2, nrow = 2,
-  vjust = 1,
-  widths = c(2, 2),
-  align = "hv",
-  common.legend = TRUE, legend = "bottom"
-  )
-
-```
-
-### Distribution average employee salary
 ```{r salary_distribution, echo=FALSE, fig.width=10, fig.height=4}
@@
   labs(title="Salary Distributions in Treated Group", x="Regions", y="Hourly rate")+
-  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ # add dots
+  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01, binwidth =1)+ # add dots
   theme_economist()
@@
                outlier.shape=5,
-               outlier.size=4) +
+               outlier.size=4)+
   labs(title="Salary Distributions in Control Group", x="Regions", y="Hourly rate")+
-  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ #add dots
+  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01,binwidth =1)+ #add dots
   theme_economist()
@@
 
+```{r franchise, echo=FALSE, fig.width=10, fig.height=4}
+
+Pie1<-control_data%>%
+  ggplot(aes(x = control_data$Q4 ,fill = Q4)) +
+  geom_bar(stat = "count", position = "dodge") +
+  coord_polar("y", start=0)+   #Create a pie chart based on the barplot
+  labs(title = "Franchise restaurants slightly decrease in treated group ",x="Regions",y="Count in control group") +
+  theme_minimal() +
+  scale_fill_manual(values = c("Red", "Blue"))
+
+Pie2<-treated_data%>%
+  ggplot(aes(x = treated_data$Q4 ,fill = Q4)) +
+  geom_bar(stat = "count", position = "dodge") +
+  coord_polar("y", start=0)+
+  labs(title = "",x="Regions", y="Count in treated group") +
+  theme_minimal() +
+  scale_fill_manual(values = c("Red", "Blue"))
+
+#Merge twp graphs
+ggarrange(
+  Pie1, Pie2, 
+  ncol = 2, nrow = 1,
+  hjust = -0.5,
+  align = "hv"
+  )
+```
+
+```{r employee#, echo=FALSE, fig.width=10, fig.height=4}
+cxc <- 
+  simulated_data%>%
+  ggplot(aes(x = simulated_data$Q8 ,fill = type)) +
+  geom_bar(width = 0.7,position = "dodge") + 
+  coord_polar()+
+  scale_fill_manual(values = c("Red", "Blue"))+
+  labs(title = "Almost 0 restaurant has more than 30 employees in control group",x="", y="Count") +
+  theme_minimal()
+
+cxc
+```
+
+### T-Test
+```{r ttest,echo=FALSE}
+#install.packages("broom")
+library(broom)
+revenue_c <- control_data$Q13
+revenue_t <- treated_data$Q13
+t<-t.test(revenue_t, revenue_c)
+m<-tidy(t, digits=1)
+m%>%
+  select(-c(estimate,statistic,parameter))%>%
+  rename(
+    mean_of_Treated=estimate1,
+    mean_of_Control=estimate2
+  )%>%
+  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
+  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
+  kable_styling()
+
+```
+The T Test is used to compare the sample mean of our Treated group and Control group.
+The goal is to determine whether the intervention has an effective effect on the treated group.
+Our hypothesis is the intervention will have positive impact towards the restaurant's revenue.
+[@kim2015t] The T test results is represented in the Table2(Table \@ref(tab:ttest)).
+The package **Broom**[@broom1] is used to clean the t test results and convert it into the dataframe.
+The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant).[@kim2015t] So we can
+interpret hypothesis not rejected which means the intervention has a significant effect on treated group.
+
+### Invention effect on Revenue distributions
+
+```{r revenue_distribution, fig.cap="Revenue distribution",echo=FALSE}
+
+library(ggthemes)
+# Treated group
+rd1<-
+  ggplot(simulated_data, aes(x = simulated_data$Q13/1000, fill=type)) +
+  geom_histogram(position = "dodge", bins = 30,binwidth = 5) +
+  scale_fill_manual(values = c("red", "blue"))+
+  labs(title="Revenue Distributions Move to the right", x="Renvenue (Thousands)", y="Count")+
+  geom_density()+
+  theme_calc()
+
+rd1
+
+```
+Two merged histograms charts were used to illustrate the restaurant's revenue distribution.
+
+(Figure \@ref(fig:revenue_distribution))
+
+### Invention effect on Flex and fiexed cost
+
+```{r felx_fix, echo=FALSE, fig.width=6, fig.height=4}
+# Treated group
+
+# Fixed costs 
+fixc1<-
+  ggplot(simulated_data, aes(fill= type, x=Q11)) +
+  geom_bar(stat="count", width = 0.6,position = "dodge")+
+  scale_fill_manual(values = c("red", "blue"))+
+    ggtitle("Fixed costs increased in treated group and remain same in control group") +
+    coord_flip()+
+    xlab("Changes")+
+    ylab("Number of restaurants")+
+    theme_minimal()
+fixc1<- fixc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title
+
+# flex cost
+flexc1<-
+    ggplot(simulated_data, aes(fill= type, x=Q12)) +
+    geom_bar(stat="count", width = 0.7, position = "dodge")+
+    scale_fill_manual(values = c("red", "blue"))+
+    ggtitle("Flexible costs increased in most of treated group restaurants") +
+    coord_flip()+
+    xlab("Changes")+
+    ylab("Number of restaurants")+
+    theme_minimal()
+flexc1<- flexc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title
+
+# combine two diagram in one graph
+ggarrange(
+  flexc1,fixc1,
+  ncol = 1, nrow = 2,
+  vjust = 1,
+  widths = c(2, 2),
+  align = "hv",
+  common.legend = TRUE, legend = "bottom"
+  )
+
+```
+
 ### correlation matrix
-```{r correlation, echo=FALSE, fig.width=20, fig.height=20}
+```{r correlation, echo=FALSE, fig.width=20, fig.height=10}
 #install.packages("fastDummies")
 library(fastDummies)
-Dummy_data<-simulated_data[-c(1,2,10)]
+Dummy_data<-treated_data[-c(1,2)] #Remove Type and postcode columns
 
-Dummy_data<- fastDummies::dummy_cols(Dummy_data)
+Dummy_data<- fastDummies::dummy_cols(Dummy_data) #  change categorical var to factors
 
-# correlation matrix for Big restaurants
-Dummy_data<-Dummy_data[-c(1:3,5:10,12,43)]
+# correlation matrix for restaurants in treated group
+Dummy_data<-Dummy_data[-c(1:3,5:7,9:11,13,44)] # remove big restaurant, cause it will always has -1 relationship with small restaurant
 
 # Compute a correlation matrix
-corr <- round(cor(Dummy_data), 1)
+corr <- round(cor(Dummy_data), 1) # round to 1 digit
 
@@
   )
-corr.plot1
 
-# correlation matrix for Small restaurants
-Dummy_data<-simulated_data[-c(1,2,10)]
-Dummy_data<- fastDummies::dummy_cols(Dummy_data)
-Dummy_data<-Dummy_data[-c(1:3,5:10,12,42)]
+# correlation matrix for restaurants in control group
+Dummy_data<-control_data[-c(1,2)] #Remove Type and postcode columns
+
+Dummy_data<- fastDummies::dummy_cols(Dummy_data) #  change categorical var to factors
+
+Dummy_data<-Dummy_data[-c(1:3,5:7,9:11,13,44)]
 
 # Compute a correlation matrix
-corr <- round(cor(Dummy_data), 1)
+corr <- round(cor(Dummy_data), 1) # round to 1 digit
 
 # Compute a matrix of correlation p-values
+#install.packages("ggcorrplot")
 library(ggcorrplot)
@@
   )
-corr.plot2
-
 # combine two diagram in one graph
@@
   corr.plot1, corr.plot2, 
-  labels = c('Big restaurant', 'Small restaurant'),
+  labels = c('Treated group', 'Control group'),
   ncol = 2, nrow = 1,

### 2021-02-26 outputs/Paper.Rmd
update

@@
 * `type` : Categorical identifier [“Treated” or “Control”] for each observation 
-* `Q1` : First three digitals of the postcode 
+* `Q1` : First three digits of the postcode 
 * `Q2` : Categorical identifier for distinguishing the type of restaurants 
@@
 
-```{r restaurant_number, echo=FALSE, fig.width=6, fig.height=5}
+Taking a deep look at all the features from survey questionnaire, we learned some demographic features about the restaurants in GTA:
+
+* From figure1(Figure \@ref(fig:restaurant number)) and figure2(Figure \@ref(fig:restaurant_type)), we noticed that more restaurants are located in Toronto (around 500) and Peel (around 400).
+The number of restaurants in Hilton is similar to the number in Durham.
+Meanwhile, Casual dining takes the lead in the restaurant type in GTA, with around 26%.
+Then it comes to Family style restaurant, accounting for 20%.
+Fast food restaurant, fine dining restaurant and Premium casual restaurant almost equally make up 10%.
+There is no big difference between treated group and control group in terms of restaurant number and type distributions.
+
+```{r restaurant number, fig.cap = "Restaurant numbers and types", echo=FALSE,fig.width=8, fig.height=5}
 R1<-simulated_data%>%
@@
   )
+
 ```
 
-```{r restaurant_type, echo=FALSE,fig.width=12, fig.height=4}
+```{r restaurant_type, fig.cap = "Restaurant types", echo=FALSE,fig.width=12, fig.height=4}
 
@@
 
-```{r salary_distribution, echo=FALSE, fig.width=10, fig.height=4}
+* In terms of employees salary, the average hourly rate before and after intervention is both around 17 CAD.
+In contrast with two boxplots, we can see there is a slight increase in the treated group.
+The reason behind might because the employee take more risks to go for work, accordingly they will receive higher salary.
+(Figure \@ref(fig:salary_distribution))
+
+```{r salary_distribution, fig.cap = "Employee salary distribution",echo=FALSE, fig.width=10, fig.height=4}
 library(ggthemes)
@@
 
-```{r franchise, echo=FALSE, fig.width=10, fig.height=4}
+* The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor.
+From the pie charts (Figure \@ref(fig:franchise)), we found the portion of franchise rate in treated group is slightly lower than control group.
+We assume in treated group, the branch franchise restaurants should follow the rules by the head office.
+Considering the potential cost of Covid issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.
+
+```{r franchise, fig.cap = "Restaurant franchise distribution",echo=FALSE, fig.width=10, fig.height=4}
 
@@
 ```
+* The polar chart illustrates the employee numbers distribution, as can be seen in figure 5.
+(Figure \@ref(fig:employee)) Because of COVID rule, no restaurant is allowed to open for large group dine in.
+So in the control group, there is 0 restaurant which has more than 30 employees.
+Most of restaurant has 10 to 20 employees.
 
-```{r employee#, echo=FALSE, fig.width=10, fig.height=4}
+```{r employee, fig.cap = "Empoyee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}
 cxc <- 
@@
 ### T-Test
-```{r ttest,echo=FALSE}
+The T Test is used to compare the sample mean of our Treated group and Control group.
+The goal is to determine whether the intervention has an effective effect on the treated group.
+Our hypothesis is the intervention will have positive impact towards the restaurant's revenue.
+[@kim2015t] The T test results is represented in the Table2(Table \@ref(tab:ttest)).
+The package **Broom**[@broom1] is used to clean the t test results and convert it into the dataframe.
+The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant).[@kim2015t] So we can
+interpret hypothesis not rejected which means the intervention has a significant effect on treated group.
+
+```{r ttest, echo=FALSE}
 #install.packages("broom")
@@
 ```
-The T Test is used to compare the sample mean of our Treated group and Control group.
-The goal is to determine whether the intervention has an effective effect on the treated group.
-Our hypothesis is the intervention will have positive impact towards the restaurant's revenue.
-[@kim2015t] The T test results is represented in the Table2(Table \@ref(tab:ttest)).
-The package **Broom**[@broom1] is used to clean the t test results and convert it into the dataframe.
-The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant).[@kim2015t] So we can
-interpret hypothesis not rejected which means the intervention has a significant effect on treated group.
 
@@
 
-```{r revenue_distribution, fig.cap="Revenue distribution",echo=FALSE}
+```{r revenue_distribution, fig.cap="Invention effect on Revenue distributions",echo=FALSE}
 
@@
 
-```{r felx_fix, echo=FALSE, fig.width=6, fig.height=4}
+```{r felx_fix, fig.cap = "Invention effect on Flex and fiexed cost",echo=FALSE, fig.width=6, fig.height=4}
 # Treated group
@@
 
-### correlation matrix
-```{r correlation, echo=FALSE, fig.width=20, fig.height=10}
+### Correlation matrix
+```{r correlation, fig.cap = "Correlation matrix",echo=FALSE, fig.width=20, fig.height=10}
 #install.packages("fastDummies")

### 2021-02-26 outputs/Paper.Rmd
update

@@
 
-* From figure1(Figure \@ref(fig:restaurant number)) and figure2(Figure \@ref(fig:restaurant_type)), we noticed that more restaurants are located in Toronto (around 500) and Peel (around 400).
+* From figure1(Figure \@ref(fig:restaurant1)) and figure2(Figure \@ref(fig:restaurant2)), we noticed that more restaurants are located in Toronto (around 500) and Peel (around 400).
 The number of restaurants in Hilton is similar to the number in Durham.
@@
 
-```{r restaurant number, fig.cap = "Restaurant numbers and types", echo=FALSE,fig.width=8, fig.height=5}
+```{r restaurant1, fig.cap = "Restaurant numbers and types", echo=FALSE,fig.width=8, fig.height=5}
 R1<-simulated_data%>%
@@
 
-```{r restaurant_type, fig.cap = "Restaurant types", echo=FALSE,fig.width=12, fig.height=4}
+```{r restaurant2, fig.cap = "Restaurant types", echo=FALSE,fig.width=12, fig.height=4}
 
@@
 The reason behind might because the employee take more risks to go for work, accordingly they will receive higher salary.
-(Figure \@ref(fig:salary_distribution))
+(Figure \@ref(fig:salary))
 
-```{r salary_distribution, fig.cap = "Employee salary distribution",echo=FALSE, fig.width=10, fig.height=4}
+```{r salary, fig.cap = "Employee salary distribution",echo=FALSE, fig.width=10, fig.height=4}
 library(ggthemes)
@@
 We assume in treated group, the branch franchise restaurants should follow the rules by the head office.
-Considering the potential cost of Covid issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.
+Considering the potential cost of COVID issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.
 

### 2021-02-26 outputs/Paper.Rmd
update

@@
   theme_minimal() +
-  scale_fill_manual(values = c("Red", "Blue"))
+  scale_fill_manual(values = c("#E85C34", "#2C92D5"))
 
@@
 * The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor.
-From the pie charts (Figure \@ref(fig:franchise)), we found the portion of franchise rate in treated group is slightly lower than control group.
+From the pie charts, we found the portion of franchise rate in treated group is slightly lower than control group.
 We assume in treated group, the branch franchise restaurants should follow the rules by the head office.
@@
 
-```{r franchise, fig.cap = "Restaurant franchise distribution",echo=FALSE, fig.width=10, fig.height=4}
+(Figure \@ref(fig:pie1))
+
+```{r pie1, fig.cap = "Restaurant franchise distribution",echo=FALSE, fig.width=10, fig.height=4}
 
@@
   coord_polar()+
-  scale_fill_manual(values = c("Red", "Blue"))+
+  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
   labs(title = "Almost 0 restaurant has more than 30 employees in control group",x="", y="Count") +
@@
   geom_histogram(position = "dodge", bins = 30,binwidth = 5) +
-  scale_fill_manual(values = c("red", "blue"))+
+  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
   labs(title="Revenue Distributions Move to the right", x="Renvenue (Thousands)", y="Count")+
@@
   geom_bar(stat="count", width = 0.6,position = "dodge")+
-  scale_fill_manual(values = c("red", "blue"))+
+  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
     ggtitle("Fixed costs increased in treated group and remain same in control group") +
@@
     geom_bar(stat="count", width = 0.7, position = "dodge")+
-    scale_fill_manual(values = c("red", "blue"))+
+    scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
     ggtitle("Flexible costs increased in most of treated group restaurants") +

### 2021-02-26 outputs/Paper.Rmd
update

@@
 Considering the potential cost of COVID issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.
-
 (Figure \@ref(fig:pie1))
 
-```{r pie1, fig.cap = "Restaurant franchise distribution",echo=FALSE, fig.width=10, fig.height=4}
+```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=10, fig.height=4}
 
@@
 ```
-* The polar chart illustrates the employee numbers distribution, as can be seen in figure 5.
+* The polar chart illustrates the employee numbers distribution, as can be seen in figure below.
 (Figure \@ref(fig:employee)) Because of COVID rule, no restaurant is allowed to open for large group dine in.
@@
 
-### Invention effect on Revenue distributions
+### Correlation matrix
+Correlation matrix shows internal relationships between x variables and y variable.
+(Figure \@ref(fig:correlation)) Intensity is indicated by the color(from red to blue).
+No significant coeffiency   is barred with symbol "x".
+More detailed analysis will be conducted in finding part.
 
-```{r revenue_distribution, fig.cap="Invention effect on Revenue distributions",echo=FALSE}
+```{r correlation, fig.cap = "Correlation matrix",echo=FALSE, fig.width=10, fig.height=10}
+#install.packages("fastDummies")
+library(fastDummies)
+Dummy_data<-simulated_data[-c(1,2)] #Remove Type and postcode columns
 
-library(ggthemes)
-# Treated group
-rd1<-
-  ggplot(simulated_data, aes(x = simulated_data$Q13/1000, fill=type)) +
-  geom_histogram(position = "dodge", bins = 30,binwidth = 5) +
-  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
-  labs(title="Revenue Distributions Move to the right", x="Renvenue (Thousands)", y="Count")+
-  geom_density()+
-  theme_calc()
+Dummy_data<- fastDummies::dummy_cols(Dummy_data) #  change categorical var to factors
 
-rd1
+# correlation matrix for restaurants in treated group
+Dummy_data<-Dummy_data[-c(1:3,5:7,9:11,13,44)] # remove big restaurant, cause it will always has -1 relationship with small restaurant
+
+# Compute a correlation matrix
+corr <- round(cor(Dummy_data), 1) # round to 1 digit
+
+# Compute a matrix of correlation p-values
+#install.packages("ggcorrplot")
+library(ggcorrplot)
+p.mat <- cor_pmat(Dummy_data)
+
+# Visualize the lower triangle of the correlation matrix
+# Barring the no significant coefficient
+ggcorrplot(
+  corr, hc.order = TRUE, type = "lower",
+  p.mat=p.mat,
+  title = "Correlation Matrix"
+  )
 
 ```
-Two merged histograms charts were used to illustrate the restaurant's revenue distribution.
 
-(Figure \@ref(fig:revenue_distribution))
+# Discussion
 
-### Invention effect on Flex and fiexed cost
+## Overview
+
+## Findings
+
+### Finding ONE
+
+### Finding TWO
+Invention effect on Flex and fiexed cost
 
@@
 ```
+### Finding THREE
+Invention effect on Revenue distributions
 
-### Correlation matrix
-```{r correlation, fig.cap = "Correlation matrix",echo=FALSE, fig.width=20, fig.height=10}
-#install.packages("fastDummies")
-library(fastDummies)
-Dummy_data<-treated_data[-c(1,2)] #Remove Type and postcode columns
+```{r revenue_distribution, fig.cap="Invention effect on Revenue distributions",echo=FALSE}
 
-Dummy_data<- fastDummies::dummy_cols(Dummy_data) #  change categorical var to factors
+library(ggthemes)
+# Treated group
+rd1<-
+  ggplot(simulated_data, aes(x = simulated_data$Q13/1000, fill=type)) +
+  geom_histogram(position = "dodge", bins = 30,binwidth = 5) +
+  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
+  labs(title="Revenue Distributions Move to the right", x="Renvenue (Thousands)", y="Count")+
+  geom_density()+
+  theme_calc()
 
-# correlation matrix for restaurants in treated group
-Dummy_data<-Dummy_data[-c(1:3,5:7,9:11,13,44)] # remove big restaurant, cause it will always has -1 relationship with small restaurant
-
-# Compute a correlation matrix
-corr <- round(cor(Dummy_data), 1) # round to 1 digit
-
-# Compute a matrix of correlation p-values
-#install.packages("ggcorrplot")
-library(ggcorrplot)
-p.mat <- cor_pmat(Dummy_data)
-
-# Visualize the lower triangle of the correlation matrix
-# Barring the no significant coefficient
-corr.plot1 <- ggcorrplot(
-  corr, hc.order = TRUE, type = "lower",
-  p.mat=p.mat
-  )
-
-# correlation matrix for restaurants in control group
-Dummy_data<-control_data[-c(1,2)] #Remove Type and postcode columns
-
-Dummy_data<- fastDummies::dummy_cols(Dummy_data) #  change categorical var to factors
-
-Dummy_data<-Dummy_data[-c(1:3,5:7,9:11,13,44)]
-
-# Compute a correlation matrix
-corr <- round(cor(Dummy_data), 1) # round to 1 digit
-
-# Compute a matrix of correlation p-values
-#install.packages("ggcorrplot")
-library(ggcorrplot)
-p.mat <- cor_pmat(Dummy_data)
-
-# Visualize the lower triangle of the correlation matrix
-# Barring the no significant coefficient
-corr.plot2 <- ggcorrplot(
-  corr, hc.order = TRUE, type = "lower",
-  p.mat=p.mat
-  )
-# combine two diagram in one graph
-
-ggarrange(
-  corr.plot1, corr.plot2, 
-  labels = c('Treated group', 'Control group'),
-  ncol = 2, nrow = 1,
-  align = "hv"
-  )
+rd1
 
 ```
-
-# Discussion
-
-## Overview
-
-## Findings
-
-### Finding ONE
-
-### Finding TWO
-
-### Finding THREE
-
 ## Limitation

### 2021-02-26 outputs/Paper.Rmd
histogram for salary distribution

@@
 
+```{r salary_distribution, echo=FALSE}
+ggplot(simulated_data, aes(x = simulated_data$Q9, fill=type)) +
+  geom_histogram(position = "dodge", bins = 30,binwidth = 0.5) +
+  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
+  labs(title="Salary Distributions Shifts to Right", x="Salary", y="Number of employee")+
+  geom_density()
+
+```
+
 # Discussion

### 2021-02-26 outputs/Paper.Rmd
histogram update

--- 2021-02-26 outputs/Paper.Rmd
@@
 
+```{r salary_distribution, echo=FALSE}
+ggplot(simulated_data, aes(x = simulated_data$Q9, fill=type)) +
+  geom_histogram(position = "dodge", bins = 30,binwidth = 0.5) +
+  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
+  labs(title="The Salary Distributions was higher for Teatment Group", x="Salary", y="Number of employee")+
+  geom_density()
+
+```
+
 # Discussion

### 2021-02-26 outputs/Paper.Rmd
diagram update

--- 2021-02-26 outputs/Paper.Rmd
@@
 ```{r read_data, include=FALSE}
-
 setwd("~/Downloads/Git/groupproject-")
@@
 
+```{r salary distribution, echo=FALSE}
+sd1<-
+  ggplot(simulated_data, aes(x = simulated_data$Q9, fill=type)) +
+  geom_histogram(position = "dodge", bins = 30,binwidth = 0.5) +
+  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
+  labs(title="The Salary Distributions was higher for Teatment Group", x="Salary", y="Number of employee")+
+  geom_density()
+```
+
 ```{r salary, fig.cap = "Employee salary distribution",echo=FALSE, fig.width=10, fig.height=4}
@@
 
-```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=10, fig.height=4}
+```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=7, fig.height=15}
 
@@
 
-```{r employee, fig.cap = "Empoyee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}
+```{r employee, fig.cap = "Employee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}
 cxc <- 

### 2021-02-26 outputs/Paper.Rmd
diagram updates

@@
   scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
-  labs(title="The Salary Distributions was higher for Teatment Group", x="Salary", y="Number of employee")+
+  labs(title="The salary distributions was higher for teatment group", x="Salary", y="Number of employee")+
   geom_density()
+sd1
 ```

### 2021-02-26 outputs/Paper.Rmd
upload intervention and method with citation

@@
 # Data 
+In this report, we use the R statistical programming language [@citeR].
+To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  ADD ANY PACKAGE HERE.
+The survey conducted by Petit Poll collects the following data:
+
+* Geographical information (FSA, Region)
+* Type of restaurant (Fast food, fast casual, casual dining, premium casual, family style, fine dining)
+* Number of years opened so far
+* Services provided (delivery, take-out)
+* Number of employees and salary of employee
+* Cost to run the restaurant (Fixed, variable)
+* Revenue per month
+* Potential COVID-19 cases
+
+[Appendix C](#appendixC) shows screen captures of the online version of the survey.In addition, we consulted several open datasets about the health inspection from each region. (CITATION)
+
+The data section illustrates the intervention and data gathering methodology. Also, we describe detailed information on our dataset, with several data visualizations such as tables and graphs.
 
@@
 
+In this experiment, we conducted a randomized controlled trial and randomly assigned subjects to two groups: the treatment group and the control group.
+Within this experiment, the treatment group receives an intervention and the control group is not being treated.
+
+In our case, the intervention is having restaurants open for indoor dining.
+Our experimental subjects are restaurants in the GTA that are currently in operation.
+We assumed all restaurants in Ontario are closed for indoor dining at the moment.
+During the shut-down, all restaurants in the control group were forbidden to offer dine-in and patio services according to the COVID-19 lockdown policy set out by the Ontario government [@citenews].
+However, take-out and delivery services were acceptable.
+Our intervention involves randomly selecting restaurants to reopen for indoor dining in the GTA.
+The restaurants in the treatment and control group were picked through stratified sampling.
+This experiment was conducted by Petit Poll and was authorized by the Ontario Department of Public Health.
+
+We randomized the control and treatment groups through stratified sampling.
+In other words, we divided all restaurants in Ontario into smaller strata.
+Each strata was grouped based on region.
+After stratification, we took random samples from each region, in proportion to its share of the population within the total population [@citeSRS].
+The distribution of all strata shows as following (see more information in [Appendix A](#appendixA)):
+
+* Toronto - 29.5%
+* Durham - 12.8%
+* York - 21.9%
+* Peel - 24.6%
+* Halton - 11%
+
+We then use a random number generator to randomly select a certain number of restaurants from a list of restaurants that was ordered alphanumerically.
+This list was procured by health inspection records that indicate all of the open restaurants within each region.
+Procedurally, we set the minimum number and the maximum number based on the number of restaurants within the given list.
+If the randomly generated number was 59, we chose the 59th restaurant in the list.
+We repeated the process until the treatment group and the control group were established with the corresponding number of restaurants.
+
+To ensure the separation of treatment and non-treatment groups, we relied on stratified random sampling based on regions.
+After stratification, the number of restaurants in the treatment and control groups were the same.
+This ensures that the treatment is the only source of potential differences in outcomes between the two groups and not based on convenience of access for citizens within each region [@citeSRS].
+Moreover, ad-hoc analysis showed that the proportion of restaurant types were the same between control and treatment groups.
+This reduces the likelihood that citizens would migrate between groups for particular restaurant types.
+
+The experiment ran for two and a half months from December 1, 2020 to February 15th, 2021.
+We distributed a consent form to 11,325 restaurants within the GTA on December 1st, 2020, and received 3,454 responses to participate in our survey by December 15th, 2020.
+We randomly sampled an equal number of respondents into the treatment group and control group.
+On December 16th, the intervention was announced for the selected 1,637 restaurants in the treatment group.
+We reserved half a month for the restaurant to prepare for reopening.
+The treatment group reopened the restaurant from January 1st to January 31st, 2021.
+We considered one month as the minimum effective period for a validity reopening.
+During the intervention, all restaurants in the treatment group were allowed to offer dine-in, patio services, delivery service, and takeout services.
+The survey itself was conducted for a half month from February 1st, 2021 to February 15th, 2021.
+Finally, we collected 3,274 responses in total from both the treatment group and control group by February 15th, 2021.
+
 ## Data Gathering Method
+
+The population included all restaurants in the GTA, excluding the ones that were completely closed.
+The sampling frame was all restaurants listed in the health inspection reporting program of all five regions.
+Currently, GTA has approximately 25,351 restaurants, including 7500 in Toronto, 3260 in Durham, 5553 in York, 6235 in Peel, and 2803 in Halton.
+We use a stratified sampling method to randomly select restaurants in each region.
+We sent consent forms to 11,325 restaurants, and received 3,454 responses, which reflects a 30.5% response rate.
+The final sample was 3,274 restaurants that responded to the paper survey.
+We arrived at 3000 as a sample size to ensure enough statistical power in our sample.
+
+We use stratified random sampling to obtain a sample that best represents the entire population.
+Unlike simple random sampling, which randomly selects data from the entire population, stratified random sampling takes each stratum in direct proportion to the population in each region compared to the total population in GTA.
+Stratified random sampling reflects the population more accurately than simple random sampling.
+With simple random sampling, it is not guaranteed that any particular subgroup or type of restaurant is chosen [@citeprocon].
+In contrast, SRS ensures each subgroup within the population has proper representation within the sample.
+In other words, it captures key population characteristics in the sample.
+Stratification gives a smaller error in estimation and greater precision than the simple random sampling method.
+The greater the differences between the strata, the greater the gain in precision[@citeSRS1].
+
+The collection instrument for this survey was paper questionnaires sent by mail.
+We first sent consent forms to obtain permission within the early stages of the experiment to randomly selected restaurants in a list of all restaurants per region.
+We did not use electronic questionnaires or surveys sent by email in order to prevent a non-response bias from the few restaurants that do not have a commercial email address or who don’t check their email frequently.
+Additionally, we avoided choosing in-person interviews in order to reduce close contact and lessen the chance of virus transmission.
+
+The total estimated cost was approximately \$20,958.
+To be specific, the average cost to print a page for black and white is around 5 cents [@citeprintcost].
+According to Stamps, the cost of a one-ounce First Class Mail stamp is \$0.55 for one way [@citestampcost].
+Each envelope cost 15 cents [@citeenevlopcost].
+We sent 11,000 informed consents first, and then sent 3454 paper surveys after.
+When we mail the consent form and survey, we include a prepaid envelope with a stamp in each single package to encourage survey response.
+Therefore, we spent \$15,950 on consent forms and \$5,008 on paper surveys.
+See more details in [Appendix B](#appendixB).
+
+We took three steps to deal with the non-responses.
+First of all, we tested the survey before sending them out.
+We kept the survey short.
+A one-minute survey normally has a higher response rate than a 15 minutes survey [@citenonresponse].
+Besides, we sent reminders to the participants through mail or phone, if we did not receive responses in the first week.
+It ensured the surveys were sent to the right address.
+In addition, we would offer incentives in exchange for completing the survey.
+
+During the early stage of designing the survey, we determined that it was unnecessary to collect the personal information of the restaurant owner.
+Also, the survey did not ask the restaurant's name and address but only the first three digits of postal code (FSA code), which encodes region-level information.
+The survey was conducted anonymously; therefore, the risk of unauthorized collection, use, and disclosure of personal information was kept to a minimum.
+
+We did not use an electronic questionnaire sent by email.
+An email survey will require participants to send their responses back to us by personal email.
+Meanwhile, physical questionnaires can be sent back anonymously, without the sender's name and return address.
+
+In the questionnaire, most questions are multiple-choice, and we were not asking any open-end questions about the personal experience.
+In particular, when it comes to the cost structure of restaurant operations, which is deemed as sensitive questions by business owners, only the direction of change was asked instead of a specific amount.
+Thus, it would be impossible to reverse engineer the financial details and to infer private attributes about restaurants such as store names and locations using this dataset.
+
+When conducting the survey, we strictly follow the terms of reference for the safe collection, retention, use, disclosure, and disposal of personal information, in accordance with the Act.
+During the survey, we reviewed the term of reference periodically.
+At the final stage of the experiment, we checked all conditions and made sure they were fully complied with.
+
+Participation in the survey was considered on a voluntary basis.
+Thus, we sent out the informed consent in order to provide participants as much information as possible.
+The consent should include the following:
+
+* The main purpose of the research.
+* The name of the institution that conducts the research.
+* How the information will be disclosed.
+* How much time the survey will take. 
+* How the respondent will be informed about the final result.
+
+We have also considered how the data will be stored for future use.
+All data will be replaced with code and stored separately from the survey response.
+Petit Poll  will be responsible for ensuring the confidentiality, integrity, and accessibility of the dataset under supervision of the Ontario government.
 
@@
 ```{r read_data, include=FALSE}
+
 setwd("~/Downloads/Git/groupproject-")
@@
 
-## Appendix A
+## Appendix A {#appendixA}
 ```{r AppendixA, message=FALSE, echo = FALSE}
@@
 
-## Appendix B
+## Appendix B {#appendixB}
 ```{r AppendixB, message=FALSE, echo = FALSE}
@@
 ```
+## Appendix C: Screenshot of the survey
 

### 2021-02-26 outputs/Paper.Rmd
citation updates

@@
 
-[Appendix C](#appendixC) shows screen captures of the online version of the survey.In addition, we consulted several open datasets about the health inspection from each region. (CITATION)
+[Appendix C](#appendixC) shows screen captures of the online version of the survey.In addition, we consulted several open datasets about the health inspection from each region, including Peel[@citePeel], Halton[@citeHalton], York [@citeYork], Durham [@citeDurham], and Toronto [@citeToronto].
 

### 2021-02-26 outputs/Paper.Rmd
update

@@
 In this report, we use the R statistical programming language [@citeR].
-To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  ADD ANY PACKAGE HERE.
+To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1] ADD ANY PACKAGE HERE.
 The survey conducted by Petit Poll collects the following data:
@@
   geom_density()
-sd1
 ```
@@
 
-```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=7, fig.height=15}
+```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=10, fig.height=5}
 
@@
 ```
+
 * The polar chart illustrates the employee numbers distribution, as can be seen in figure below.

### 2021-02-26 outputs/Paper.Rmd
update

@@
 
-* The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor.
-From the pie charts, we found the portion of franchise rate in treated group is slightly lower than control group.
+* The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor.[@nhamo2020restaurants] From the pie charts, we found the portion of franchise rate in treated group is slightly lower than control group.
 We assume in treated group, the branch franchise restaurants should follow the rules by the head office.
@@
 (Figure \@ref(fig:employee)) Because of COVID rule, no restaurant is allowed to open for large group dine in.
+For large size restaurant, they all make corresponding actions to reduce their flexiable costs, such as reduce the full time employees.
 So in the control group, there is 0 restaurant which has more than 30 employees.

### 2021-02-26 outputs/Paper.Rmd
Added report and reference citation for Discussion

--- 2021-02-26 outputs/Paper.Rmd
@@
 # Data
-In this report, we use the R statistical programming language [@citeR].
-To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  ADD ANY PACKAGE HERE.
-The survey conducted by Petit Poll collects the following data:
-
-* Geographical information (FSA, Region)
-* Type of restaurant (Fast food, fast casual, casual dining, premium casual, family style, fine dining)
-* Number of years opened so far
-* Services provided (delivery, take-out)
-* Number of employees and salary of employee
-* Cost to run the restaurant (Fixed, variable)
-* Revenue per month
-* Potential COVID-19 cases
-
-[Appendix C](#appendixC) shows screen captures of the online version of the survey.In addition, we consulted several open datasets about the health inspection from each region, including Peel[@citePeel], Halton[@citeHalton], York [@citeYork], Durham [@citeDurham], and Toronto [@citeToronto].
-
-The data section illustrates the intervention and data gathering methodology. Also, we describe detailed information on our dataset, with several data visualizations such as tables and graphs.
 
@@
 
-In this experiment, we conducted a randomized controlled trial and randomly assigned subjects to two groups: the treatment group and the control group.
-Within this experiment, the treatment group receives an intervention and the control group is not being treated.
-
-In our case, the intervention is having restaurants open for indoor dining.
-Our experimental subjects are restaurants in the GTA that are currently in operation.
-We assumed all restaurants in Ontario are closed for indoor dining at the moment.
-During the shut-down, all restaurants in the control group were forbidden to offer dine-in and patio services according to the COVID-19 lockdown policy set out by the Ontario government [@citenews].
-However, take-out and delivery services were acceptable.
-Our intervention involves randomly selecting restaurants to reopen for indoor dining in the GTA.
-The restaurants in the treatment and control group were picked through stratified sampling.
-This experiment was conducted by Petit Poll and was authorized by the Ontario Department of Public Health.
-
-We randomized the control and treatment groups through stratified sampling.
-In other words, we divided all restaurants in Ontario into smaller strata.
-Each strata was grouped based on region.
-After stratification, we took random samples from each region, in proportion to its share of the population within the total population [@citeSRS].
-The distribution of all strata shows as following (see more information in [Appendix A](#appendixA)):
-
-* Toronto - 29.5%
-* Durham - 12.8%
-* York - 21.9%
-* Peel - 24.6%
-* Halton - 11%
-
-We then use a random number generator to randomly select a certain number of restaurants from a list of restaurants that was ordered alphanumerically.
-This list was procured by health inspection records that indicate all of the open restaurants within each region.
-Procedurally, we set the minimum number and the maximum number based on the number of restaurants within the given list.
-If the randomly generated number was 59, we chose the 59th restaurant in the list.
-We repeated the process until the treatment group and the control group were established with the corresponding number of restaurants.
-
-To ensure the separation of treatment and non-treatment groups, we relied on stratified random sampling based on regions.
-After stratification, the number of restaurants in the treatment and control groups were the same.
-This ensures that the treatment is the only source of potential differences in outcomes between the two groups and not based on convenience of access for citizens within each region [@citeSRS].
-Moreover, ad-hoc analysis showed that the proportion of restaurant types were the same between control and treatment groups.
-This reduces the likelihood that citizens would migrate between groups for particular restaurant types.
-
-The experiment ran for two and a half months from December 1, 2020 to February 15th, 2021.
-We distributed a consent form to 11,325 restaurants within the GTA on December 1st, 2020, and received 3,454 responses to participate in our survey by December 15th, 2020.
-We randomly sampled an equal number of respondents into the treatment group and control group.
-On December 16th, the intervention was announced for the selected 1,637 restaurants in the treatment group.
-We reserved half a month for the restaurant to prepare for reopening.
-The treatment group reopened the restaurant from January 1st to January 31st, 2021.
-We considered one month as the minimum effective period for a validity reopening.
-During the intervention, all restaurants in the treatment group were allowed to offer dine-in, patio services, delivery service, and takeout services.
-The survey itself was conducted for a half month from February 1st, 2021 to February 15th, 2021.
-Finally, we collected 3,274 responses in total from both the treatment group and control group by February 15th, 2021.
-
 ## Data Gathering Method
-
-The population included all restaurants in the GTA, excluding the ones that were completely closed.
-The sampling frame was all restaurants listed in the health inspection reporting program of all five regions.
-Currently, GTA has approximately 25,351 restaurants, including 7500 in Toronto, 3260 in Durham, 5553 in York, 6235 in Peel, and 2803 in Halton.
-We use a stratified sampling method to randomly select restaurants in each region.
-We sent consent forms to 11,325 restaurants, and received 3,454 responses, which reflects a 30.5% response rate.
-The final sample was 3,274 restaurants that responded to the paper survey.
-We arrived at 3000 as a sample size to ensure enough statistical power in our sample.
-
-We use stratified random sampling to obtain a sample that best represents the entire population.
-Unlike simple random sampling, which randomly selects data from the entire population, stratified random sampling takes each stratum in direct proportion to the population in each region compared to the total population in GTA.
-Stratified random sampling reflects the population more accurately than simple random sampling.
-With simple random sampling, it is not guaranteed that any particular subgroup or type of restaurant is chosen [@citeprocon].
-In contrast, SRS ensures each subgroup within the population has proper representation within the sample.
-In other words, it captures key population characteristics in the sample.
-Stratification gives a smaller error in estimation and greater precision than the simple random sampling method.
-The greater the differences between the strata, the greater the gain in precision[@citeSRS1].
-
-The collection instrument for this survey was paper questionnaires sent by mail.
-We first sent consent forms to obtain permission within the early stages of the experiment to randomly selected restaurants in a list of all restaurants per region.
-We did not use electronic questionnaires or surveys sent by email in order to prevent a non-response bias from the few restaurants that do not have a commercial email address or who don’t check their email frequently.
-Additionally, we avoided choosing in-person interviews in order to reduce close contact and lessen the chance of virus transmission.
-
-The total estimated cost was approximately \$20,958.
-To be specific, the average cost to print a page for black and white is around 5 cents [@citeprintcost].
-According to Stamps, the cost of a one-ounce First Class Mail stamp is \$0.55 for one way [@citestampcost].
-Each envelope cost 15 cents [@citeenevlopcost].
-We sent 11,000 informed consents first, and then sent 3454 paper surveys after.
-When we mail the consent form and survey, we include a prepaid envelope with a stamp in each single package to encourage survey response.
-Therefore, we spent \$15,950 on consent forms and \$5,008 on paper surveys.
-See more details in [Appendix B](#appendixB).
-
-We took three steps to deal with the non-responses.
-First of all, we tested the survey before sending them out.
-We kept the survey short.
-A one-minute survey normally has a higher response rate than a 15 minutes survey [@citenonresponse].
-Besides, we sent reminders to the participants through mail or phone, if we did not receive responses in the first week.
-It ensured the surveys were sent to the right address.
-In addition, we would offer incentives in exchange for completing the survey.
-
-During the early stage of designing the survey, we determined that it was unnecessary to collect the personal information of the restaurant owner.
-Also, the survey did not ask the restaurant's name and address but only the first three digits of postal code (FSA code), which encodes region-level information.
-The survey was conducted anonymously; therefore, the risk of unauthorized collection, use, and disclosure of personal information was kept to a minimum.
-
-We did not use an electronic questionnaire sent by email.
-An email survey will require participants to send their responses back to us by personal email.
-Meanwhile, physical questionnaires can be sent back anonymously, without the sender's name and return address.
-
-In the questionnaire, most questions are multiple-choice, and we were not asking any open-end questions about the personal experience.
-In particular, when it comes to the cost structure of restaurant operations, which is deemed as sensitive questions by business owners, only the direction of change was asked instead of a specific amount.
-Thus, it would be impossible to reverse engineer the financial details and to infer private attributes about restaurants such as store names and locations using this dataset.
-
-When conducting the survey, we strictly follow the terms of reference for the safe collection, retention, use, disclosure, and disposal of personal information, in accordance with the Act.
-During the survey, we reviewed the term of reference periodically.
-At the final stage of the experiment, we checked all conditions and made sure they were fully complied with.
-
-Participation in the survey was considered on a voluntary basis.
-Thus, we sent out the informed consent in order to provide participants as much information as possible.
-The consent should include the following:
-
-* The main purpose of the research.
-* The name of the institution that conducts the research.
-* How the information will be disclosed.
-* How much time the survey will take. 
-* How the respondent will be informed about the final result.
-
-We have also considered how the data will be stored for future use.
-All data will be replaced with code and stored separately from the survey response.
-Petit Poll  will be responsible for ensuring the confidentiality, integrity, and accessibility of the dataset under supervision of the Ontario government.
 
@@
 ```{r read_data, include=FALSE}
-
-setwd("~/Downloads/Git/groupproject-")
+#setwd("~/Downloads/Git/groupproject-")
 
@@
 From the pie charts, we found the portion of franchise rate in treated group is slightly lower than control group.
-We assume in treated group, the branch franchise restaurants should follow the rules by the head office.
-Considering the potential cost of COVID issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.
+We assume in treated group, the branch franchise restaurants must follow the rules and policies set by their head office.
+[find a reference] Considering the potential cost of COVID issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.
 (Figure \@ref(fig:pie1))
@@
 ```
-* The polar chart illustrates the employee numbers distribution, as can be seen in figure below.
-(Figure \@ref(fig:employee)) Because of COVID rule, no restaurant is allowed to open for large group dine in.
+* The polar bar graph illustrates the distribution of employee numbers, as can be shown in figure below.
+(Figure \@ref(fig:employee)) Because of the COVID lockdown restriction, no restaurant is allowed to open for large group dine-in or outdoor patio, which in turn causes the layoff in servers.
+In particular, large restaurants would want to further cut labor costs by laying off extra helpers in the kitchen to maintain only essential operations for food production.
 So in the control group, there is 0 restaurant which has more than 30 employees.
-Most of restaurant has 10 to 20 employees.
+Most of the restaurants have 10 to 20 employees, as a result of labor force layoff.
 
@@
 ### T-Test
-The T Test is used to compare the sample mean of our Treated group and Control group.
+The t-test is used to compare the sample mean of our Treated group and Control group.
 The goal is to determine whether the intervention has an effective effect on the treated group.
 Our hypothesis is the intervention will have positive impact towards the restaurant's revenue.
-[@kim2015t] The T test results is represented in the Table2(Table \@ref(tab:ttest)).
-The package **Broom**[@broom1] is used to clean the t test results and convert it into the dataframe.
+[@kim2015t] The t-test results is represented in the Table2(Table \@ref(tab:ttest)).
+The package **Broom** [@broom1] is used to clean the t test results and convert it into the dataframe.
 The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant).[@kim2015t] So we can
-interpret hypothesis not rejected which means the intervention has a significant effect on treated group.
+interpret hypothesis not rejected which means that the re-opening of restaurants has a significant effect on treated group in terms of revenue increase.
 
@@
 ### Correlation matrix
-Correlation matrix shows internal relationships between x variables and y variable.
-(Figure \@ref(fig:correlation)) Intensity is indicated by the color(from red to blue).
-No significant coeffiency   is barred with symbol "x".
+Correlation matrix shows internal relationships between restaurant feature variables and our variable of interest, restaurant revenue.
+(Figure \@ref(fig:correlation)) Intensity and direction of relationship is indicated by the color scale from red to blue (+1 to -1.
+descendant).
+Categorical variables are encoded to factors.
+Insignificant coefficient is barred with symbol "x".
 More detailed analysis will be conducted in finding part.
@@
 
-### Finding ONE
+### Finding ONE: Higher salary and more job opportunities in treatment group
 
-### Finding TWO
-Invention effect on Flex and fiexed cost
+The treated restaurants have been opening for in-door dining and patio for a month while the control group must comply with the lockdown policy during COVID-19 second waves in GTA.
+The additional operating channels (in-door dining and patio) demand rehiring of previously layoff servers in the dining rooms and extra chefs in the kitchen.
+Under the surging demand for labor force and the potential risk due to exposure to human-contact, the restaurants have to offer higher salaries to compensate for employees’ potential risk of infection and entice them away from competitor restaurants.
+From the salary distribution boxplots (Figure \@ref(fig:Salary)) we can see that overall salary pay levels are higher in the treatment group across 5 regions in GTA, including average rate and all other distribution percentiles.
+As for job opportunities, the treated restaurants hire more labor force.
+To cater to the increased demand from dine-in orders, the open restaurants hire more servers and chefs, which result in a size expansion in the number of employees.
+The number of restaurants having more than 10 employees are larger in the treatment group, whereas there are no restaurants operating with more than 30 employees in the control group.
+(Figure \@ref(fig:employee))
 
-```{r felx_fix, fig.cap = "Invention effect on Flex and fiexed cost",echo=FALSE, fig.width=6, fig.height=4}
+### Finding TWO: Cost structure changes in treatment group
+
+Labor cost is one of the main components of variable cost for restaurants.
+The hiring surge for the restaurants open for dine-in increases the expenditure on human capital and thus an increase in variable cost.
+In addition, dine-in and patio options potentially increase the demand for food ingredients, which is another major source of variable cost.
+As a result, most of the open restaurants have increased variable costs.
+For fixed costs, about half of the open restaurants experience a cost increase and the other half have no change in fixed costs.
+(Figure \@ref(fig:var_fix))
+
+```{r var_fix, fig.cap = "Invention effect on Variable and Fixed cost",echo=FALSE, fig.width=6, fig.height=4}
 # Treated group
@@
     scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
-    ggtitle("Flexible costs increased in most of treated group restaurants") +
+    ggtitle("Variable costs increased in most of treated group restaurants") +
     coord_flip()+
@@
 ```
-### Finding THREE
+
+### Finding THREE: Significant revenue increase in treatment group
+
+The re-opening implementation enables the treated restaurants to operate indoor dining and patio services besides offering delivery and/or pickup as before during lockdown.
+The additional line of business attracts more customers to visit stores to order dishes and beverages.
+The increased food sales earn extra revenue for those restaurants.
+As demonstrated through the revenue histogram (Figure \@ref(fig:revenue_distribution)), the treatment group has higher revenue levels overall than the control group.
+The restaurants follow binomial distributions based on restaurant sizes.
+Restaurant size and revenue level are positively correlated.
+According to the correlation heatmap (Figure \@ref(fig:correlation)), bigger restaurants generate more revenues than small ones.
+Restaurants having fewer than 20 employees are defined to be small, which are most of the cases in the total samples.
+Both small and big restaurants generate higher revenues in the treated group.
+The t-test [cross ref: t-table] further verifies our finding that the restaurants allowed for re-opening earn significantly more than the control group; the average revenue for the treated is \$63,144 while below \$5,000 for the control group.
+
 Invention effect on Revenue distributions
@@
 ```
+
 ## Limitation
+
+### Self-selection, late-responders and non response bias
+
+In our consent form and followup survey, 30.5% of restaurants agreed to participate in our survey and 180 subjects dropped out in the survey. 
+On the one hand, participants can choose whether to participate in the survey.
+It is possible that the restaurant owners who operate smoothly during lockdown are more willing to discuss the topic on restaurant operations and more likely to agree to participate in the survey.
+Upward bias can exist in the statistics for the respondents which distorts the representation for the population caused by self-selection.
+On the other hand, within the short time experiment period, we might not receive all the survey mails back because some of them respond late.
+Participants who do not respond may differ in characteristics and outcomes from those who respond.
+If that is the case, self-selection bias and non-response bias exist in the sampling procedures.
+Since we do not have data on non-responders, we cannot directly compare them with respondents to detect the bias.
+The paper claim that late-responders share similar characteristics with non-responders [@nonresponse], then the comparison can be made in order to check for potential non-response bias during data collection.
+[@preventnonres]
+
+### Response bias - desirability bias
+
+Since it is a self administered study that responders fill out the survey without an interviewer, the information reported by restaurant owners themselves may be inaccurate or even dishonest.
+Therefore, there are potential response biases such as social desirability bias and over/undervaluation, caused by the impression that responders are motivated to reinforce socially desirable behaviors and deny those that are not in their answers.
+Making the survey anonymous, employing a third party or choosing neutral tones can dis-associate sensitive questions with presumed social judgements and thus mitigate this bias.
+[@desirability]
+These methods were implemented by this survey.
+For example, the survey uses a neutral tone in questions, it did not ask for restaurant names, and the study was delegated by the Ontario government to us, a professional polling company.
+
+### Data unobtainable for those completely closed - imperfect sampling frame and potential sampling bias
+
+The choice of experiment population subjects are limited to all restaurants in GTA that are on the contact list provided by the Ontario government since the owners of restaurants that are completely closed are not reachable through mailing or phone.
+Although stratified sampling is conducted within the sampled population to ensure representativeness of the population, the excluded closed restaurants restricted our sampling coverage and made sampling procedures less random.
+{@samplingbias} If unsampled data characteristics are different from our population systematically in nature, the randomized control assumption would be weakened.
+Here we claim that our research interest lies on the impact of COVID shutdown on restaurant revenue, therefore it is reasonable to exclude the observations with null revenue.
+
+### Experiment drop-outs
+
+There are an equal number of dropouts in the control and treatment groups during the survey (90 out of 3454 in each).
+Dropout occurs for many reasons: death, no longer willing to participate, no longer available, geographic move, or negatively impacted by treatment conditions.
+[@dropout].
+Despite equal dropout rates, dropout might still affect internal validity if statistical behavior of dropouts are different from completers.
+[@diffdropout] Given that only a small portion of subjects dropped out, its impact is assumed to be negligible.
+
+### Time length of our experiment - only one month
+
+Our experiment lasts for only a month, which is the minimal duration needed in order to observe any change in monthly accounting bookkeeping settled, employee paychecks paid along with other expenditures such as rent and hydro bills.
+It may take longer to observe any seasonality and time trends that could impact the operation conditions of the restaurant industry and confound our treatment result.
+The paper argues that one month is sufficient for our research purpose since statistical significance in business operation differences can be observed in the data between two groups according to the two-sample t-test result (Table \@ref(tab:ttest))).
+
+### Privacy problem on postal code
+
+Questions on identifying information are avoided or offset to a general level to abide by research ethics.
+For example, to protect the privacy of restaurants involved in the survey, We did not ask about restaurant names, and the location of restaurants is proxied by FSA code, the first three digits of postal code, which only encodes the region-level information.
+Thereby, it would be impossible to reverse engineer the restaurant identity by any ill-intended third parties.
+Furthermore, postal code is a proxy for socioeconomic status.
+Wealth level would confound the restaurant’s choice of location and its ability to pay rent and attract high-end customers, which correlates with revenue and eventually biases the model.
+[@zipcode] Consequently, the privacy concern is addressed by the use of FSA code.
+
+### Rough geographic representation by FSA
+Due to the limited geographic location information about restaurants, the exploratory spatial analysis on restaurant location distributions can not be realized.
+The FSA code only provides the region-level information, which is not detailed enough to plot a heat map.
+However, weighing the importance of data privacy in survey ethics, this limitation in rough geographic representation is negligible.
 
@@
 
-```{r}
+After addressing potential biases and limitations in our experiment design, we state that those problems are mitigated by our design in sampling, data gathering, and survey process under the Randomized Controlled Trial framework.
+There are no systematic biases in the experiment process, the variable features are randomized, and the restaurants in control and treatment groups share similar underlying characteristics other than the external implementation of reopening policy.
+Therefore the internal validity of treatment effect on variable of interest holds.
+[@RCT] The only source of variation in restaurant revenue comes from our treatment of reopening the restaurant for full-operation.
+Next we would like to explore the alternatives in enhancing our study from the aspect of external validity and quantitative modeling.
 
-```
+### External validity
+
+In order for the findings to be generalizable to other situations and settings in the real world, experiments should be conducted in broader scales and longer durations.
+[@externalv] The choice of population could be every restaurant outside of GTA across provinces in Canada in order to control for region-specific influence on the restaurant industry.
+The experiment time frame can be prolonged to year-base, or multiple monthly experiments can be conducted in random months and compare their final result to rule out the time trend effect on restaurant business operations.
+
+### Model building
+
+In order to quantify the extent of statistical influence of each feature on the operating of restaurants besides the treatment effect of opening restaurants we have observed with the experiment treatment, linear regression and feature importance metrics can be applied in building a statistical model.
+Statistical inference can further identify the individual; statistical significant factors that cause variations in restaurants revenues.
+Along with our Randomized Control Trial experiment framework, the study would provide our client, the Ontario government, with an insightful understanding of the effect of COVID-19 shut-downs on restaurant businesses.
 
@@
 
-## Appendix A {#appendixA}
+## Appendix A
 ```{r AppendixA, message=FALSE, echo = FALSE}
@@
 
-## Appendix B {#appendixB}
+## Appendix B
 ```{r AppendixB, message=FALSE, echo = FALSE}
@@
 ```
-## Appendix C: Screenshot of the survey
 

### 2021-02-26 outputs/Paper.Rmd
update

--- 2021-02-26 outputs/Paper.Rmd
@@
 In this report, we use the R statistical programming language [@citeR].
-To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1] ADD ANY PACKAGE HERE.
+To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1], "ggthemes" is used to change the diagram theme.
+[@themes]ADD ANY PACKAGE HERE.
 The survey conducted by Petit Poll collects the following data:
@@
 library(fastDummies)
-Dummy_data<-simulated_data[-c(1,2)] #Remove Type and postcode columns
+Dummy_data<-simulated_data[-c(1,2)] %>% #Remove Type and postcode columns
+rename(
+  Region = Q2,
+  operation_years = Q5,
+  Hourly_rate = Q9,
+  Total_renvenue =Q13,
+  Type=Q3,
+  Fanchise= Q4,
+  Takeout=Q6,
+  Delivery=Q7,
+  Size=Q8,
+  COVID = Q10,
+  Fixed=Q11,
+  Flex=Q12
+)
 
@@
 Dummy_data<-Dummy_data[-c(1:3,5:7,9:11,13,44)] # remove big restaurant, cause it will always has -1 relationship with small restaurant
+
+Dummy_data<-   # change column names
+  Dummy_data
 

### 2021-02-27 outputs/Paper.Rmd
update

@@
 library(tidyverse)
+library(here)
 #install.packages("PerformanceAnalytics")
@@
   select(-size)%>%
+  rename(
+  Region = Q2,
+  operation_years = Q5,
+  Hourly_rate = Q9,
+  Total_renvenue =Q13,
+  Type=Q3,
+  Fanchise= Q4,
+  Takeout=Q6,
+  Delivery=Q7,
+  Size=Q8,
+  COVID = Q10,
+  Fixed_Cost=Q11,
+  Flex_Cost=Q12,
+  PostCode=Q1)%>%
   kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
@@
 
-R2<-simulated_data%>%
-  ggplot(aes(x = simulated_data$Q3 ,fill = type)) +
-  geom_bar(stat = "count", position = "dodge") +
-  labs(title = "More restuarants in GTA are casual dinning ",x="Regions") +
-  theme_minimal() +
-  scale_fill_manual(values = c("#E85C34", "#2C92D5"))
-
-# combine two diagram in one graph
-ggarrange(
-  R1,R2,
-  ncol = 1, nrow = 2,
-  vjust = 1,
-  widths = c(2, 2),
-  align = "hv",
-  common.legend = TRUE, legend = "bottom"
-  )
-
+R1
 ```
@@
 * In terms of employees salary, the average hourly rate before and after intervention is both around 17 CAD.
-In contrast with two boxplots, we can see there is a slight increase in the treated group.
-The reason behind might because the employee take more risks to go for work, accordingly they will receive higher salary.
-(Figure \@ref(fig:salary))
+In contrast with two boxplots (Figure \@ref(fig:salary2)), we can see there is a slight increase in the treated group.
+The reason behind might because the employee take more risks to go for work, accordingly they will receive higher salary(Figure \@ref(fig:salary1)).
 
-```{r salary distribution, echo=FALSE}
+```{r salary1, fig.cap = "Salary Distribution", echo=FALSE,fig.width=12, fig.height=4}
 sd1<-
@@
   geom_density()
+
+sd1
 ```
 
-```{r salary, fig.cap = "Employee salary distribution",echo=FALSE, fig.width=10, fig.height=4}
+```{r salary2, fig.cap = "Employee salary distribution",echo=FALSE, fig.width=10, fig.height=4}
 library(ggthemes)
@@
 
-* The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor.[@nhamo2020restaurants] From the pie charts, we found the portion of franchise rate in treated group is slightly lower than control group.
+* The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor.[@nhamo2020restaurants] From the pie charts(Figure \@ref(fig:pie1)), we found the portion of franchise rate in treated group is slightly lower than control group.
 We assume in treated group, the branch franchise restaurants should follow the rules by the head office.
 Considering the potential cost of COVID issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.
-(Figure \@ref(fig:pie1))
 
@@
 
-* The polar chart illustrates the employee numbers distribution, as can be seen in figure below.
-(Figure \@ref(fig:employee)) Because of COVID rule, no restaurant is allowed to open for large group dine in.
-For large size restaurant, they all make corresponding actions to reduce their flexiable costs, such as reduce the full time employees.
+* The polar bar graph illustrates the distribution of employee numbers, as can be shown in figure below (Figure \@ref(fig:employee)).
+Because of the COVID lockdown restriction, no restaurant is allowed to open for large group dine-in or outdoor patio, which in turn causes the layoff in servers.
+In particular, large restaurants would want to further cut labor costs by laying off extra helpers in the kitchen to maintain only essential operations for food production.
 So in the control group, there is 0 restaurant which has more than 30 employees.
-Most of restaurant has 10 to 20 employees.
+Most of the restaurants have 10 to 20 employees, as a result of labor force layoff.
 
@@
 
-### Finding ONE
+### Finding ONE: Higher salary and more job opportunities in treatment group
 
-### Finding TWO
-Invention effect on Flex and fiexed cost
+The treated restaurants have been opening for in-door dining and patio for a month while the control group must comply with the lockdown policy during COVID-19 second waves in GTA.
+The additional operating channels (in-door dining and patio) demand rehiring of previously layoff servers in the dining rooms and extra chefs in the kitchen.
+Under the surging demand for labor force and the potential risk due to exposure to human-contact, the restaurants have to offer higher salaries to compensate for employees’ potential risk of infection and entice them away from competitor restaurants.
+From the salary distribution boxplots (Figure \@ref(fig:Salary2)) we can see that overall salary pay levels are higher in the treatment group across 5 regions in GTA, including average rate and all other distribution percentiles.
+As for job opportunities, the treated restaurants hire more labor force.
+To cater to the increased demand from dine-in orders, the open restaurants hire more servers and chefs, which result in a size expansion in the number of employees.
+The number of restaurants having more than 10 employees are larger in the treatment group, whereas there are no restaurants operating with more than 30 employees in the control group.
+(Figure \@ref(fig:employee))
 
-```{r felx_fix, fig.cap = "Invention effect on Flex and fiexed cost",echo=FALSE, fig.width=6, fig.height=4}
+### Finding TWO: Cost structure changes in treatment group
+
+Labor cost is one of the main components of variable cost for restaurants.
+The hiring surge for the restaurants open for dine-in increases the expenditure on human capital and thus an increase in variable cost.
+In addition, dine-in and patio options potentially increase the demand for food ingredients, which is another major source of variable cost.
+As a result, most of the open restaurants have increased variable costs.
+For fixed costs, about half of the open restaurants experience a cost increase and the other half have no change in fixed costs.
+(Figure \@ref(fig:var1))
+
+```{r var1, fig.cap = "Invention effect on Variable and Fixed cost",echo=FALSE, fig.width=6, fig.height=4}
 # Treated group
@@
 ```
-### Finding THREE
+
+### Finding THREE: Significant revenue increase in treatment group
+
+The re-opening implementation enables the treated restaurants to operate indoor dining and patio services besides offering delivery and/or pickup as before during lockdown.
+The additional line of business attracts more customers to visit stores to order dishes and beverages.
+The increased food sales earn extra revenue for those restaurants.
+As demonstrated through the revenue histogram (Figure \@ref(fig:revenue1)), the treatment group has higher revenue levels overall than the control group.
+The restaurants follow binomial distributions based on restaurant sizes.
+Restaurant size and revenue level are positively correlated.
+According to the correlation heatmap (Figure \@ref(fig:correlation)), bigger restaurants generate more revenues than small ones.
+Restaurants having fewer than 20 employees are defined to be small, which are most of the cases in the total samples.
+Both small and big restaurants generate higher revenues in the treated group.
+The t-test [cross ref: t-table] further verifies our finding that the restaurants allowed for re-opening earn significantly more than the control group; the average revenue for the treated is \$63,144 while below \$5,000 for the control group.
+
 Invention effect on Revenue distributions
 
-```{r revenue_distribution, fig.cap="Invention effect on Revenue distributions",echo=FALSE}
+```{r revenue1, fig.cap="Invention effect on Revenue distributions",echo=FALSE}
 

### 2021-02-27 outputs/Paper.Rmd
update

@@
 
-* From figure1(Figure \@ref(fig:restaurant1)) and figure2(Figure \@ref(fig:restaurant2)), we noticed that more restaurants are located in Toronto (around 500) and Peel (around 400).
+* From (Figure \@ref(fig:restaurant1)) and (Figure \@ref(fig:restaurant2)), we noticed that more restaurants are located in Toronto (around 500) and Peel (around 400).
 The number of restaurants in Hilton is similar to the number in Durham.
@@
 Both small and big restaurants generate higher revenues in the treated group.
-The t-test [cross ref: t-table] further verifies our finding that the restaurants allowed for re-opening earn significantly more than the control group; the average revenue for the treated is \$63,144 while below \$5,000 for the control group.
+The t-test (Table \@ref(tab:ttest)) further verifies our finding that the restaurants allowed for re-opening earn significantly more than the control group; the average revenue for the treated is \$63,144 while below \$5,000 for the control group.
 

### 2021-02-27 outputs/Paper.Rmd
update

@@
 ---
-title: "TITLE"
+title: "Opening Restaurants During COVID-19 Can Prove Beneficial for Restaurant Revenue in the GTA"
 author: "Adrian Wong, Yingying Zhou, Xinyi Xu, Yang Wu "
@@
  toc: no
-subtitle: "SUBTITLE"
-abstract: "ABSTRACT"
+subtitle: "An analysis of restaurant businesses amidst COVID-19 in the GTA"
+abstract: "Restaurant businesses are suffering in the advent of COVID-19 lockdown restrictions.
+Within this paper, a randomized controlled trial was conducted in order to explore the effects of reopening dine-in services for restaurants within the GTA.
+It was discovered that restaurants that allow for dine-in services provide higher salaries and more job opportunities on average compared to restaurants that either offer take-out or delivery services only.
+Moreover, this analysis illustrated that expense structures between restaurants are likely to shift as a result of offering dine-in services during the pandemic, such that variable costs are likely to increase.
+Ultimately, restaurants that allow patrons to dine-in see a significant increase in revenue as a result (a difference of $5000 on average).
+By analyzing this data, results may help the government enact appropriate lockdown policies that take a nuanced consideration of restaurant businesses."
+
 thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
@@
 # Introduction
-```{r}
-
-```
+Current COVID-19 lockdown policies are having a significant effect on restaurant businesses within the GTA.
+Previous research shows that over half of Canadian restaurants may be unable to operate in current conditions that were set out by the local government.
+This can be detrimental to the economic situation as restaurant businesses can contribute over 4% of the national GDP.
+As a result, the government needs to consider the business effects of these lockdown policies on restaurants across the GTA.
+A randomized controlled trial was conducted to investigate these factors.
+Within the treatment group, restaurants were given an intervention that allowed them to open for indoor/patio dining while a control group remained open only for delivery and take-out services.
+After one month, these restaurants were given a survey that asked them to indicate different business-related factors, such as their expense changes, employee salaries, revenue, and COVID-related exposures during the experimental condition.
+More details with regards to data collection, intervention, descriptive analysis, and overview of findings will be provided in subsequent sections.
+Finally, limitations of the study as well as future directions will be discussed.
+This analysis will ultimately inform decisions with regards to the severity of restrictions imposed on restaurants in the GTA during the current pandemic.
 
@@
 To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1], "ggthemes" is used to change the diagram theme.
-[@themes]ADD ANY PACKAGE HERE.
+[@themes].
 The survey conducted by Petit Poll collects the following data:
@@
 ```{r restaurant2, fig.cap = "Restaurant types", echo=FALSE,fig.width=12, fig.height=4}
+R2<-simulated_data%>%
+  ggplot(aes(x = simulated_data$Q3 ,fill = type)) +
+  geom_bar(stat = "count", position = "dodge") +
+  labs(title = "More restuarants in GTA are casual dinning ",x="Regions") +
+  theme_minimal() +
+  scale_fill_manual(values = c("#E85C34", "#2C92D5"))
 
-library(viridisLite)
-
-# Treated group
-rt1<-
-  ggplot(treated_data, aes(fill= Q3, x= Q2)) +
-  geom_bar(position="stack", stat="count")+
-    ggtitle("Treated Group: Restaurant Types") +
-    xlab("Regions")+
-    ylab("Count of Numbers")+
-    theme_grey()
-
-rt1<- rt1 + guides(fill=guide_legend(title="Types")) # change the Legend title
-
-# Control group
-rt2<-
-  ggplot(control_data, aes(fill= Q3, x= Q2)) +
-  geom_bar(position="stack", stat="count")+
-    ggtitle("Control Group: Restaurant Types") +
-    xlab("Regions")+
-    ylab("Count of Numbers")+
-    theme_grey()
-
-rt2<- rt2 + guides(fill=guide_legend(title="Types")) # change the Legend title 
-# combine two diagram in one graph
-ggarrange(
-  rt1, rt2, 
-  ncol = 2, nrow = 1,
-  vjust = 1,
-  widths = c(2, 2),
-  align = "hv",
-  common.legend = TRUE, legend = "bottom"
-  )
-
+R2
 ```
@@
 Our hypothesis is the intervention will have positive impact towards the restaurant's revenue.
-[@kim2015t] The t-test results is represented in the Table2(Table \@ref(tab:ttest)).
+[@kim2015t] The t-test results is represented in the (Table \@ref(tab:ttest)).
 The package **Broom** [@broom1] is used to clean the t test results and convert it into the dataframe.
@@
 Under the surging demand for labor force and the potential risk due to exposure to human-contact, the restaurants have to offer higher salaries to compensate for employees’ potential risk of infection and entice them away from competitor restaurants.
-From the salary distribution boxplots (Figure \@ref(fig:Salary2)) we can see that overall salary pay levels are higher in the treatment group across 5 regions in GTA, including average rate and all other distribution percentiles.
+From the salary distribution boxplots (Figure \@ref(fig:Salary2)),  we can see that overall salary pay levels are higher in the treatment group across 5 regions in GTA, including average rate and all other distribution percentiles.
 As for job opportunities, the treated restaurants hire more labor force.

### 2021-02-27 outputs/Paper.Rmd
update

@@
 
+```{r page1, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
+library(here)
+knitr::include_graphics(here::here("outputs/image/questionnaire1.png"))
+```
+
+```{r page2, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
+library(here)
+knitr::include_graphics(here::here("outputs/image/questionnaire2.png"))
+```
+
+```{r page3, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
+library(here)
+knitr::include_graphics(here::here("outputs/image/questionnaire3.png"))
+```
 \newpage

### 2021-02-27 outputs/Paper.Rmd
update

@@
 In this report, we use the R statistical programming language [@citeR].
-To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1], "ggthemes" is used to change the diagram theme.
-[@themes].
+To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1], "ggthemes" is used to change the diagram theme [@themes].
 The survey conducted by Petit Poll collects the following data:
@@
 
-[Appendix C](#appendixC) shows screen captures of the online version of the survey.In addition, we consulted several open datasets about the health inspection from each region, including Peel[@citePeel], Halton[@citeHalton], York [@citeYork], Durham [@citeDurham], and Toronto [@citeToronto].
+[Appendix C](#appendixC) shows screen captures of the online version of the survey.In addition, we consulted several open datasets about the health inspection from each region, including Peel [@citePeel], Halton [@citeHalton], York [@citeYork], Durham [@citeDurham], and Toronto [@citeToronto].
 
@@
 The goal is to determine whether the intervention has an effective effect on the treated group.
-Our hypothesis is the intervention will have positive impact towards the restaurant's revenue.
-[@kim2015t] The t-test results is represented in the (Table \@ref(tab:ttest)).
+Our hypothesis is the intervention will have positive impact towards the restaurant's revenue [@kim2015t].
+The t-test results is represented in the (Table \@ref(tab:ttest)).
 The package **Broom** [@broom1] is used to clean the t test results and convert it into the dataframe.
-The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant).[@kim2015t] So we can
+The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant)[@kim2015t].
+So we can
 interpret hypothesis not rejected which means that the re-opening of restaurants has a significant effect on treated group in terms of revenue increase.
@@
 ## Overview 
-
+Previous research has demonstrated that 60% of Canadian restaurants may be unable to operate with current policies in response to the Coronavirus within three months.
+Moreover, 1.2 million Canadians are said to be employed within the restaurant industry with an annual payroll of $30 billion.
+Restaurants contribute a significant amount to Canada’s economy, and particularly in the GTA.
+However, it is still unknown how much restaurants receive through business during the pandemic.
+According to Perrin Beatty (CEO of the Canadian Chamber of Commerce), restaurants may find it “nearly impossible” to make money during COVID-19 lockdown restrictions.
+Moreover, ongoing COVID restrictions contribute to the employment rate of the restaurant industry to fall by 21% below pre-COVID levels.
+It was predicted that half of table-service restaurants expect to reduce their employed staff due to strict lockdown policies.
+By researching the effects of allowing restaurants to offer dine-in services, we can better understand the economic impact of re-opening restaurants to the public.
+It is also important to consider the risk associated with re-opening restaurants as well.
+According to a recent model by provincial health officials, the number of restaurant-related outbreaks of COVID appear significantly lower than the number of school, child-care, or long-term care related outbreaks.
+Dr.
+Colin Furness of the University of Toronto cited that this number is an underrepresentation of restaurant related transmissions, due to a lack of contact tracing.
+As is the case, measurements of COVID-related incidents within restaurants that offer dine-in services versus restaurants that don’t may provide clarity on this matter.
+Overall, in order to decide on appropriate lockdown policies within the restaurant industry, further clarity is required to make an informed decision.
+As existing contributions rely heavily on predictive speculation, it is important to verify their claims in the most recent light (February 2021).
+Furthermore, contributions seem to apply to national restaurants across Canada more broadly.
+By applying a randomized control trial to the GTA, researchers are able to distinguish nuance at a regional level.
+This experimental method can then be applied to other areas across Canada in order to establish more appropriate government policies region by region.
 ## Findings
 
-### Finding ONE: Higher salary and more job opportunities in treatment group
+###  Higher salary and more job opportunities in treatment group
 
@@
 Under the surging demand for labor force and the potential risk due to exposure to human-contact, the restaurants have to offer higher salaries to compensate for employees’ potential risk of infection and entice them away from competitor restaurants.
-From the salary distribution boxplots (Figure \@ref(fig:Salary2)),  we can see that overall salary pay levels are higher in the treatment group across 5 regions in GTA, including average rate and all other distribution percentiles.
+From the salary distribution boxplots(Figure \@ref(fig:salary2)),  we can see that overall salary pay levels are higher in the treatment group across 5 regions in GTA, including average rate and all other distribution percentiles.
 As for job opportunities, the treated restaurants hire more labor force.
@@
 
-### Finding TWO: Cost structure changes in treatment group
+### Cost structure changes in treatment group
 
@@
 
-### Finding THREE: Significant revenue increase in treatment group
+### Significant revenue increase in treatment group
 
@@
 The t-test (Table \@ref(tab:ttest)) further verifies our finding that the restaurants allowed for re-opening earn significantly more than the control group; the average revenue for the treated is \$63,144 while below \$5,000 for the control group.
-
-Invention effect on Revenue distributions
 
@@
 Since we do not have data on non-responders, we cannot directly compare them with respondents to detect the bias.
-The paper claim that late-responders share similar characteristics with non-responders [@nonresponse], then the comparison can be made in order to check for potential non-response bias during data collection.
-[@preventnonres]
+The paper claim that late-responders share similar characteristics with non-responders [@nonresponse], then the comparison can be made in order to check for potential non-response bias during data collection [@preventnonres].
 
@@
 Therefore, there are potential response biases such as social desirability bias and over/undervaluation, caused by the impression that responders are motivated to reinforce socially desirable behaviors and deny those that are not in their answers.
-Making the survey anonymous, employing a third party or choosing neutral tones can dis-associate sensitive questions with presumed social judgements and thus mitigate this bias.
-[@desirability]
+Making the survey anonymous, employing a third party or choosing neutral tones can dis-associate sensitive questions with presumed social judgements and thus mitigate this bias [@desirability].
 These methods were implemented by this survey.
@@
 The choice of experiment population subjects are limited to all restaurants in GTA that are on the contact list provided by the Ontario government since the owners of restaurants that are completely closed are not reachable through mailing or phone.
-Although stratified sampling is conducted within the sampled population to ensure representativeness of the population, the excluded closed restaurants restricted our sampling coverage and made sampling procedures less random.
-{@samplingbias} If unsampled data characteristics are different from our population systematically in nature, the randomized control assumption would be weakened.
+Although stratified sampling is conducted within the sampled population to ensure representativeness of the population, the excluded closed restaurants restricted our sampling coverage and made sampling procedures less random [@samplingbias].
+If unsampled data characteristics are different from our population systematically in nature, the randomized control assumption would be weakened.
 Here we claim that our research interest lies on the impact of COVID shutdown on restaurant revenue, therefore it is reasonable to exclude the observations with null revenue.
@@
 There are an equal number of dropouts in the control and treatment groups during the survey (90 out of 3454 in each).
-Dropout occurs for many reasons: death, no longer willing to participate, no longer available, geographic move, or negatively impacted by treatment conditions.
-[@dropout].
-Despite equal dropout rates, dropout might still affect internal validity if statistical behavior of dropouts are different from completers.
-[@diffdropout] Given that only a small portion of subjects dropped out, its impact is assumed to be negligible.
+Dropout occurs for many reasons: death, no longer willing to participate, no longer available, geographic move, or negatively impacted by treatment conditions [@dropout].
+Despite equal dropout rates, dropout might still affect internal validity if statistical behavior of dropouts are different from completers [@diffdropout].
+Given that only a small portion of subjects dropped out, its impact is assumed to be negligible.
 
@@
 Furthermore, postal code is a proxy for socioeconomic status.
-Wealth level would confound the restaurant’s choice of location and its ability to pay rent and attract high-end customers, which correlates with revenue and eventually biases the model.
-[@zipcode] Consequently, the privacy concern is addressed by the use of FSA code.
+Wealth level would confound the restaurant’s choice of location and its ability to pay rent and attract high-end customers, which correlates with revenue and eventually biases the model [@zipcode].
+Consequently, the privacy concern is addressed by the use of FSA code.
 
@@
 There are no systematic biases in the experiment process, the variable features are randomized, and the restaurants in control and treatment groups share similar underlying characteristics other than the external implementation of reopening policy.
-Therefore the internal validity of treatment effect on variable of interest holds.
-[@RCT] The only source of variation in restaurant revenue comes from our treatment of reopening the restaurant for full-operation.
+Therefore the internal validity of treatment effect on variable of interest holds [@RCT].
+The only source of variation in restaurant revenue comes from our treatment of reopening the restaurant for full-operation.
 Next we would like to explore the alternatives in enhancing our study from the aspect of external validity and quantitative modeling.
@@
 
-In order for the findings to be generalizable to other situations and settings in the real world, experiments should be conducted in broader scales and longer durations.
-[@externalv] The choice of population could be every restaurant outside of GTA across provinces in Canada in order to control for region-specific influence on the restaurant industry.
+In order for the findings to be generalizable to other situations and settings in the real world, experiments should be conducted in broader scales and longer durations [@externalv].
+The choice of population could be every restaurant outside of GTA across provinces in Canada in order to control for region-specific influence on the restaurant industry.
 The experiment time frame can be prolonged to year-base, or multiple monthly experiments can be conducted in random months and compare their final result to rule out the time trend effect on restaurant business operations.

### 2021-02-27 outputs/Paper.Rmd
update

@@
 Current COVID-19 lockdown policies are having a significant effect on restaurant businesses within the GTA.
-Previous research shows that over half of Canadian restaurants may be unable to operate in current conditions that were set out by the local government.
-This can be detrimental to the economic situation as restaurant businesses can contribute over 4% of the national GDP.
+Previous research shows that over half of Canadian restaurants may be unable to operate in current conditions that were set out by the local government [@toronto_2020].
+This can be detrimental to the economic situation as restaurant businesses can contribute over 4% of the national GDP [@lew_2020].
 As a result, the government needs to consider the business effects of these lockdown policies on restaurants across the GTA.
@@
 Previous research has demonstrated that 60% of Canadian restaurants may be unable to operate with current policies in response to the Coronavirus within three months.
-Moreover, 1.2 million Canadians are said to be employed within the restaurant industry with an annual payroll of $30 billion.
+Moreover, 1.2 million Canadians are said to be employed within the restaurant industry with an annual payroll of $30 billion [@toronto_2020].
 Restaurants contribute a significant amount to Canada’s economy, and particularly in the GTA.
 However, it is still unknown how much restaurants receive through business during the pandemic.
-According to Perrin Beatty (CEO of the Canadian Chamber of Commerce), restaurants may find it “nearly impossible” to make money during COVID-19 lockdown restrictions.
+According to Perrin Beatty (CEO of the Canadian Chamber of Commerce), restaurants may find it “nearly impossible” to make money during COVID-19 lockdown restrictions [@toronto_2020].
 Moreover, ongoing COVID restrictions contribute to the employment rate of the restaurant industry to fall by 21% below pre-COVID levels.
-It was predicted that half of table-service restaurants expect to reduce their employed staff due to strict lockdown policies.
+It was predicted that half of table-service restaurants expect to reduce their employed staff due to strict lockdown policies [@restaurants_canada].
 By researching the effects of allowing restaurants to offer dine-in services, we can better understand the economic impact of re-opening restaurants to the public.
@@
 Dr.
-Colin Furness of the University of Toronto cited that this number is an underrepresentation of restaurant related transmissions, due to a lack of contact tracing.
+Colin Furness of the University of Toronto cited that this number is an underrepresentation of restaurant related transmissions, due to a lack of contact tracing [@declerq_2020].
 As is the case, measurements of COVID-related incidents within restaurants that offer dine-in services versus restaurants that don’t may provide clarity on this matter.

### 2021-02-27 scripts/00_response_simulation.R
update

@@ -1,351 +1,0 @@
-#### Preamble ####
-# Purpose: This script simulates the responses to a survey about restaurants in Toronto.
-# Author: Yingying Zhou, Xinyi Xu, Adrian Wong
-# Data: 14 February 2021
-# Contact: yingying.zhou@utoronto.ca; xiny.xu@mail.utoronto.ca; adr.wong@mail.utoronto.ca 
-# License: MIT
-# Pre-requisites: 
-# - None
-
-
-#### Workspace setup ####
-library(tidyverse)
-#install.packages("here")
-library(here)
-
-
-# For Q2: first three digits of your postal code?
-# Function that takes a region and generates a random FSA code within that region
-# An FSA code is the first three letters of a postal code
-fsa_generate <- function(region) {
-  
-  # Toronto FSAs
-  if(region=="Toronto") {
-    return(paste("M", sample(c(0:9), 1), sample(LETTERS, 1), sep = ""))
-    
-    # Durham FSAs
-  } else if(region=="Durham") {
-    m <- sample(c(1, 9, 0), 1)
-    if (m==1){
-      l <- sample(c('G','H','J','K','L','M','N','P','R','V','W','X','Y','S','T','Z','B'), 1)
-    } else if(m==9){
-      l <- sample(c('P', 'L'), 1)
-    } else {
-      l <- sample(c('B','E','C'), 1)
-    }
-    return(paste("L", m, l, sep = ""))
-    
-    # York FSAs
-  } else if(region=="York") {
-    m <- sample(c(0, 3, 4, 6, 7, 9), 1)
-    if (m==0){
-      l <- sample(c('H','E','G','J','N'), 1)
-    } else if(m==3){
-      l <- sample(c('P', 'R','S','X','Y','Z'), 1)
-    } else if(m==4){
-      l <- sample(c('A','B','C','E','S','G','H','L','P'), 1)
-    } else if(m==6){
-      l <- sample(c('A','B','C','E','G'), 1)
-    } else if(m==7){
-      l <- sample(c('B', 'E'), 1)
-    } else {
-      l = "N"
-    }
-    return(paste("L", m, l, sep = ""))
-    
-    # Peel FSAs 
-  } else if(region=="Peel") {
-    m <- sample(c(4, 5, 6, 7), 1)
-    if (m==4){
-      l <- sample(c('T','V','W','X','Y','Z'), 1)
-    } else if(m==5){
[…]

### 2021-02-27 scripts/survey_response_simulation.R

@@ -90,20 +90,57 @@ fsa_generate <- function(region) {
 
 
 #### Simulate questions ####
-# Q1: What is the first three digits of your postal code?
+# Q1: What is the first three digits of your postal code? 
+
+# source from: https://en.wikipedia.org/wiki/List_of_postal_codes_of_Canada:_L
+
 # Q2: Which municipality is your restaurant located in?
+
+# source from:https://www.google.com/url?q=https://www.toronto.ca/311/knowledgebase/kb/docs/articles/economic-development-and-culture/program-support/number-of-restaurants-in-toronto.html%23:~:text%3DApproximately%25207%252C500&sa=D&source=editors&ust=1614396911629000&usg=AOvVaw2PeiaPLBOEmvvJhAM3z6Y_
+
 # Q3: What is the type of your restaurant?
+
+# source from: https://www.scrapehero.com/top-fast-food-chains-in-canada/
+
 # Q4: Is your restaurant a franchise?
+
+# source from: http://www.franchise101.net/canadian-franchise-statistics
+
 # Q5: How long has your restaurant been open (in years)?
+
+# source from: https://www.lightspeedhq.com/blog/why-do-restaurants-fail/
+
 # Q6: Have you offered a takeout service in the past month?
+
+# source from: https://www.zomato.com/toronto/restaurants
+
 # Q7: Have you offered a delivery service in the past month?
+
+# source from: https://www.doordash.com/en-CA
+
 # Q8: Number of employees in the restaurant
+
+# source from: https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1410002301&pickMembers%5B0%5D=1.7&pickMembers%5B1%5D=2.1&pickMembers%5B2%5D=4.1&pickMembers%5B3%5D=5.1&cubeTimeFrame.startYear=2016&cubeTimeFrame.endYear=2020&referencePeriods=20160101%2C20200101
+
 # Q9: On average, how much do your restaurant employees earn per hour ($CAD)?
+
+# source from: https://ca.indeed.com/career/restaurant-staff/salaries/Durham--ON?from=top_sb
+
 # Q10: Has your restaurant been a site of a potential COVID case?
+
+# source from: https://ottawa.ctvnews.ca/bars-restaurants-account-for-2-per-cent-of-covid-19-outbreaks-in-ottawa-14-per-cent-in-toronto-1.5166676
+
 # Q11: How has your FIXED costs to run the restaurant changed within this month?
+
[…]

### 2021-02-27 outputs/Paper.Rmd
update!
uptade

@@
 
-thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
+thanks: 'Code and data are available at: https://github.com/yangg1224/GTA_Restaurant-.git'
 bibliography: references.bib
@@
 In this report, we use the R statistical programming language [@citeR].
-To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1], "ggthemes" is used to change the diagram theme [@themes].
+To be specific, we use the `tidyvers` package to process data [@citetidyverse], `kableExtra` package to generate tables [@citekableExtra],  `ggplot2` is used to draw diagrams [@gg1], `ggthemes` is used to change the diagram theme [@themes].
 The survey conducted by Petit Poll collects the following data:
@@
 
-setwd("~/Downloads/Git/groupproject-")
+library(here)
 
 # read raw dataset from scripts, need to run survey_response _simulation first.
-simulated_data<- read_csv("inputs/simulated_data.csv")
+simulated_data<- read_csv(here::here("inputs/simulated_data.csv"))
 

### 2021-02-27 outputs/Paper.Rmd
update

@@
   kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
-  kable_styling()
+  kable_styling( )
 

### 2021-02-27 outputs/Paper.Rmd
update

--- 2021-02-27 outputs/Paper.Rmd
@@
   kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
-  kable_styling()
+  kableExtra::kable_styling(latex_options = c("hold_position"))
 
@@
 ## Appendix A {#appendixA}
-```{r AppendixA, message=FALSE, echo = FALSE}
+```{r AppendixA, message=FALSE,echo = FALSE}
 ### Number in GTA ### 
@@
   Number_of_Region = c (number_of_Toronto,number_of_Durham,number_of_York,number_of_Peel,number_of_Halton,number_of_GTA),
-  Proportion_of_Region= c (proportion_Toronto,proportion_Durham,proportion_York,proportion_Peel,proportion_Halton,Proportion_GTA)%>% round(digits = 2),
-  Sample_of_Region = c (sample_Toronto,sample_Durham,sample_York ,sample_Peel,sample_Halton,number_of_sample) %>% round(digits = 0)
+  Proportion_of_Region= c (proportion_Toronto,proportion_Durham,proportion_York,proportion_Peel,proportion_Halton,Proportion_GTA)%>% round(digits = 2), Sample_of_Region = c (sample_Toronto,sample_Durham,sample_York ,sample_Peel,sample_Halton,number_of_sample) %>% round(digits = 0)
   )
@@
                col.names = c("Region", "Number of Restuarants", "Proportion(%)", "Sample Selected"))%>%
-  kable_styling()
+  kableExtra::kable_styling(latex_options = c("hold_position"))
 ```
@@
                col.names = c("Components", "Cost per unit", "Total cost for each component"))%>%
-  kable_styling()
+  kableExtra::kable_styling(latex_options = c("hold_position"))
 
 ```
-## Appendix C: Screenshot of the survey
+
+\newpage
+## Appendix C:
 
